### 2024-06-06 manuscript/Manuscript.qmd
MS: update of fig1

---
title: "New paper template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: 
    embed-resources: true
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

# Abstract

[This]{.underline} is an R **Markdown** *document.* ^Markdown^ is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

**text in bold** *italic* [underline]{.underline}

# Introduction

You can add references either by referring to their id in the .bib file e.g., [@Marinkovi2020], or by switching to the visual editor (Cogwheel in the .Rmd menu -\> Use Visual Editor). [@Jokura_2023][@Jokura_2023][@Jacobs2023]

It is now a test to edit the text and see how the changes show up on GitHub.

Test of git show.

In the visual editor mode, go to 'Insert' -\> \@ Citation

You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]

The easiest way is to use the command line:

```{bash}
#| echo: true
#| eval: false

curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.91258.1 >> references.bib
```

*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]

The references are stored in manuscript/references.bib (need to be defined in the Yaml header). This file will automatically updated when you insert a new reference through the Visual editor \> Insert \> Citations.

[@ozpolat2021][@Wu2020; @Saile2023; @Lohmann2023][@lohmann2001]

In this documents, references will be formatted in the style of eLife. This is defined in the Yaml header under: csl: elife.csl. The elife.csl file is saved in the /manuscript folder.

If you would like to use a different citation format, download the respective .csl file (e.g., from the Zotero style repository <https://www.zotero.org/styles>), save it in the /manuscript folder of the project and change the Yaml to csl: your_favourite_journal.csl.

## Results

Inserting Figures <!--# I don't agree here -->

Test comment here. <!--# Hi -->

You can add your figures into the rendered document. We saved the figures into /manuscript/figures or /manuscript/figure_supplements and can insert them from there. We use knitr::include_graphics for this. The title and legend can also be edited, as will as the width of the output figure. Test comment behaviour: <!--# Test comment for git show -->

```{r}
#| echo: false
#| eval: false
print("hi")
```

```{r, out.width = "100%", fig.cap="**Figure 1. A figure** (A) A nice picture. (B) legend.  (C) <br> (D) " }
#| echo: false

knitr::include_graphics("figures/Figure1.png")
```

```{r, out.width = "100%", fig.cap="**Figure 1. Our nice figure from yesterday** (A) A nice picture. (B) legend.  (C) <br> (D) " }
#| echo: false 
#| warning: false

knitr::include_graphics("figures/Figure_complex.png")
```

## Equations

Equations can also be inserted, Insert -\> Display Math:

$$
\bar{X} = \frac{\sum_{i=1}^{n} x_{i}}{n}
$$

\

## Sourcing code and working with variable

```{r}
#| include: false
#| eval: true
source(here::here("analysis/scripts/statistics_for_paper.R"))
```

The mean value of Nanog expression was `r Nanog_mean` indicating that Nanog is downregulated. The 'analysis/scripts/statistics_for_paper.R' script is sourced and it runs but the output is not included in the knitted output. But we can access the variables defined in the sourced script simply by adding \` r var_name \` between \` backticks, in this case max_PRC value is `r max_PRC` (now this number comes from our sourced script).

If we update the data, the script can recalculate the variable we want to refer to in the text and update the number.

## Acknowledgements

We would like to thank the Jekely lab for the R project template (<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by ...

## Materials and Methods

You can insert tables from source data, such as .csv or Excel files and render them in html with the tinytable package.

Alternatively, you can use the Markdown grid table format. For more complex tables, you can use the [tablesgenerator](https://www.tablesgenerator.com/markdown_tables) online grid table editor/converter (e.g. converts csv or excel files).

The output may differ between html and pdf, for most consistent results use the grid table format described [here](https://quarto.org/docs/authoring/tables.html).

**Key Resources Table**

```{r tt, echo=FALSE, eval=TRUE}
#| fig-pos: "h"

library(readxl)
library(tinytable)

#read data
resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")

tt(resources_table, theme = "grid", width = 1, placement = "H")

```

| Col1 | Col2 | Col3 | Col4 | Col5 |
|------|------|------|------|------|
| a    | b    | c    | d    | e    |
| d    |      |      |      |      |

: Grid Table example {tbl-colwidths="\[10,20,20,20,30\]"}

## Complex grid table example

This table was generated by tt() as the output of an r chunk in a Quarto doc. For larger multi-page tables, this method gives correct page breaks in the pdf and html outputs. You can change the relative column widths with {tbl-colwidths="\[10,20,20,20,30\]"} placed after the table caption declaration at the end.

| Reagent type (species) or resource   | Designation                                    | Source or reference                                                                      | Identifiers | Additional information                                                                                           |
|---------------|---------------|---------------|---------------|---------------|
| biological sample (N. vectensis)     | larval, juvenile and adult N. vectensis        | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter | N/A         | NA                                                                                                               |
| biological sample (cDNA)             | cDNA obtained from N. vectensis                | this study                                                                               | N/A         | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
| biological sample (peptide extract)  | peptide extracts obtained from N. vectensis    | this study                                                                               | N/A         | Peptides extracted from N. vectensis according to protocol explained in Material and Methods                     |
| genetic reagent (cDNA synthesis)     | SuperScript™ III First-Strand Synthesis System | Invitrogen (from ThermoFisher)                                                           | 18080051    | NA                                                                                                               |
| genetic reagent (Polymerase)         | Q5® Hot Start High-Fidelity DNA Polymerase     | New England Biolabs                                                                      | M0493L      | NA                                                                                                               |
| genetic reagent (DNA assembly)       | NEBuilder® HiFi DNA Assembly Master Mix        | New England Biolabs                                                                      | E2621L      | NA                                                                                                               |
| genetic reagent (restriction enzyme) | EcoRV restriction enzyme                       | New England Biolabs                                                                      | R3195L      | NA                                                                                                               |
| genetic reagent (restriction enzyme) | Afl2 restriction enzyme                        | New England Biolabs                                                                      | R0520L      | NA                                                                                                               |

: More complex Grid Table example {tbl-colwidths="\[10,20,20,20,30\]"}

## References

```{=html}
<!--
## See https://github.com/hypothesis/client
## Add commenting functionality with this script
-->
```
```{=html}
<script src="hypothes.is/embed.js" async></script>
```

### 2024-06-06 manuscript/Manuscript.tex
COS course day 2 updates

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
]{article}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Arial}
  \setmonofont[]{DejaVu Sans Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[lmargin=0.8in,rmargin=0.8in,tmargin=0.8in,bmargin=0.8in]{geometry}
\ifLuaTeX
  \usepackage{luacolor}
  \usepackage[soul]{lua-ul}
\else
  \usepackage{soul}

\fi
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{lineno}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={New paper template},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{New paper template}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\raggedright

Author 1\textsuperscript{1,2,*} , Author 2\textsuperscript{1,2}, Author
3\textsuperscript{3}, Author 4E\textsuperscript{4}
\newline\textsuperscript{1}Heidelberg University, Centre for Organismal
Studies (COS), 69120 Heidelberg, Germany
\newline\textsuperscript{2}Affiliation 2
\newline\textsuperscript{3}Affiliation 3
\newline\textsuperscript{4}Affiliation 4\newline
\textsuperscript{*}Correspondence: xy@cos.uni-heidelberg.de}
\author{}
\date{}

\begin{document}
\maketitle

\linenumbers

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\setstretch{1.2}
\section{Abstract}\label{abstract}

\ul{This} is an R \textbf{Markdown} \emph{document.}
\textsuperscript{Markdown} is a simple formatting syntax for authoring
HTML, PDF, and MS Word documents. For more details on using R Markdown
see \url{http://rmarkdown.rstudio.com}.

\textbf{text in bold} \emph{italic} \ul{underline}

\section{Introduction}\label{introduction}

You can add references either by referring to their id in the .bib file
e.g., (Marinković et al., 2019), or by switching to the visual editor
(Cogwheel in the .Rmd menu -\textgreater{} Use Visual Editor). {[}Jokura
et al. (2023){]}(Jokura et al., 2023)(Jacobs and Ryu, 2023)

It is now a test to edit the text and see how the changes show up on
GitHub.

Test of git show.

In the visual editor mode, go to `Insert' -\textgreater{} @ Citation

You can select a Zotero library, PubMed, CrossRef etc. and insert the
citations. (Jacobs and Ryu, 2023)

The easiest way is to use the command line:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{curl} \AttributeTok{{-}LH} \StringTok{"Accept: application/x{-}bibtex"}\NormalTok{ https://doi.org/10.7554/eLife.91258.1 }\OperatorTok{\textgreater{}\textgreater{}}\NormalTok{ references.bib}
\end{Highlighting}
\end{Shaded}

\emph{Platynereis dumerilii} is a marine annelid\ldots{} (Ozpolat et
al., 2021)

The references are stored in manuscript/references.bib (need to be
defined in the Yaml header). This file will automatically updated when
you insert a new reference through the Visual editor \textgreater{}
Insert \textgreater{} Citations.

{[}Ozpolat et al. (2021){]}(Lohmann et al., 2023; Saile et al., 2023; Wu
et al., 2020)(Lohmann et al., 2001)

In this documents, references will be formatted in the style of eLife.
This is defined in the Yaml header under: csl: elife.csl. The elife.csl
file is saved in the /manuscript folder.

If you would like to use a different citation format, download the
respective .csl file (e.g., from the Zotero style repository
\url{https://www.zotero.org/styles}), save it in the /manuscript folder
of the project and change the Yaml to csl: your\_favourite\_journal.csl.

\subsection{Results}\label{results}

Inserting Figures

Test comment here.

You can add your figures into the rendered document. We saved the
figures into /manuscript/figures or /manuscript/figure\_supplements and
can insert them from there. We use knitr::include\_graphics for this.
The title and legend can also be edited, as will as the width of the
output figure. Test comment behaviour:

\begin{figure}[H]

{\centering \includegraphics[width=1\textwidth,height=\textheight]{figures/Figure1.png}

}

\caption{\textbf{Figure 1. A figure} (A) A nice picture. (B) legend. (C)
(D)}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\textwidth,height=\textheight]{figures/Figure_complex.png}

}

\caption{\textbf{Figure 1. Our nice figure from yesterday} (A) A nice
picture. (B) legend. (C) (D)}

\end{figure}%

\subsection{Equations}\label{equations}

Equations can also be inserted, Insert -\textgreater{} Display Math:

\[
\bar{X} = \frac{\sum_{i=1}^{n} x_{i}}{n}
\]

\hfill\break

\subsection{Sourcing code and working with
variable}\label{sourcing-code-and-working-with-variable}

The mean value of Nanog expression was 0.0909 indicating that Nanog is
downregulated. The `analysis/scripts/statistics\_for\_paper.R' script is
sourced and it runs but the output is not included in the knitted
output. But we can access the variables defined in the sourced script
simply by adding ` r var\_name ` between ` backticks, in this case
max\_PRC value is 21 (now this number comes from our sourced script).

If we update the data, the script can recalculate the variable we want
to refer to in the text and update the number.

\subsection{Acknowledgements}\label{acknowledgements}

We would like to thank the Jekely lab for the R project template
(\url{https://github.com/JekelyLab/new_paper_template}) we used to write
this paper. This work was funded by \ldots{}

\subsection{Materials and Methods}\label{materials-and-methods}

You can insert tables from source data, such as .csv or Excel files and
render them in html with the tinytable package.

Alternatively, you can use the Markdown grid table format. For more
complex tables, you can use the
\href{https://www.tablesgenerator.com/markdown_tables}{tablesgenerator}
online grid table editor/converter (e.g.~converts csv or excel files).

The output may differ between html and pdf, for most consistent results
use the grid table format described
\href{https://quarto.org/docs/authoring/tables.html}{here}.

\textbf{Key Resources Table}

\begin{verbatim}
Warning: The `placement` argument in `tt()` is deprecated. Please use this
instead: `theme_tt(table, 'placement')`
\end{verbatim}

\begin{table}[H]
\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
width={1\linewidth},
colspec={X[]X[]X[]X[]X[]},
hlines, vlines,
}                     %% tabularray inner close
Reagent type (species) or resource & Designation & Source or reference & Identifiers & Additional information \\
biological sample (N. vectensis)     & larval, juvenile and adult N. vectensis        & Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter & N/A      & NA                                                                                                               \\
biological sample (cDNA)             & cDNA obtained from N. vectensis                & this study                                                                               & N/A      & RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation \\
biological sample (peptide extract)  & peptide extracts obtained from N. vectensis    & this study                                                                               & N/A      & Peptides extracted from N. vectensis according to protocol explained in Material and Methods                     \\
genetic reagent (cDNA synthesis)     & SuperScript™ III First-Strand Synthesis System & Invitrogen (from ThermoFisher)                                                           & 18080051 & NA                                                                                                               \\
genetic reagent (Polymerase)         & Q5® Hot Start High-Fidelity DNA Polymerase     & New England Biolabs                                                                      & M0493L   & NA                                                                                                               \\
genetic reagent (DNA assembly)       & NEBuilder® HiFi DNA Assembly Master Mix        & New England Biolabs                                                                      & E2621L   & NA                                                                                                               \\
genetic reagent (restriction enzyme) & EcoRV restriction enzyme                       & New England Biolabs                                                                      & R3195L   & NA                                                                                                               \\
genetic reagent (restriction enzyme) & Afl2 restriction enzyme                        & New England Biolabs                                                                      & R0520L   & NA                                                                                                               \\
\end{tblr}
\end{table}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3000}}@{}}
\caption{Grid Table example}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
a & b & c & d & e \\
d & & & & \\
\end{longtable}

\subsection{Complex grid table
example}\label{complex-grid-table-example}

This table was generated by tt() as the output of an r chunk in a Quarto
doc. For larger multi-page tables, this method gives correct page breaks
in the pdf and html outputs. You can change the relative column widths
with \{tbl-colwidths=``{[}10,20,20,20,30{]}''\} placed after the table
caption declaration at the end.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3000}}@{}}
\caption{More complex Grid Table example}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Reagent type (species) or resource
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Designation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source or reference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Identifiers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Additional information
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Reagent type (species) or resource
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Designation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source or reference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Identifiers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Additional information
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
biological sample (N. vectensis) & larval, juvenile and adult N.
vectensis & Specimens obtained form the Marine Invertebrate Culture Unit
of the University of Exeter & N/A & NA \\
biological sample (cDNA) & cDNA obtained from N. vectensis & this study
& N/A & RNA extracted with Trizol and cDNA synthesized with cDNA
synthesis kit according to manufacturers recommendation \\
biological sample (peptide extract) & peptide extracts obtained from N.
vectensis & this study & N/A & Peptides extracted from N. vectensis
according to protocol explained in Material and Methods \\
genetic reagent (cDNA synthesis) & SuperScript™ III First-Strand
Synthesis System & Invitrogen (from ThermoFisher) & 18080051 & NA \\
genetic reagent (Polymerase) & Q5® Hot Start High-Fidelity DNA
Polymerase & New England Biolabs & M0493L & NA \\
genetic reagent (DNA assembly) & NEBuilder® HiFi DNA Assembly Master Mix
& New England Biolabs & E2621L & NA \\
genetic reagent (restriction enzyme) & EcoRV restriction enzyme & New
England Biolabs & R3195L & NA \\
genetic reagent (restriction enzyme) & Afl2 restriction enzyme & New
England Biolabs & R0520L & NA \\
\end{longtable}

\subsection{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Jacobs2023}
Jacobs EAK, Ryu S. 2023. Larval zebrafish as a model for studying
individual variability in translational neuroscience research.
\emph{Frontiers in Behavioral Neuroscience} \textbf{17}.
doi:\href{https://doi.org/10.3389/fnbeh.2023.1143391}{10.3389/fnbeh.2023.1143391}

\bibitem[\citeproctext]{ref-Jokura_2023}
Jokura K, Ueda N, Gühmann M, Yañez-Guerra LA, Słowiński P, Wedgwood KCA,
Jékely G. 2023. Nitric oxide feedback to ciliary photoreceptor cells
gates a UV avoidance circuit.
doi:\href{https://doi.org/10.7554/elife.91258.1}{10.7554/elife.91258.1}

\bibitem[\citeproctext]{ref-Lohmann2023}
Lohmann J, de Luxán-Hernández C, Gao Y, Zoschke R, Weingartner M. 2023.
Arabidopsis translation factor eEF1Bγ impacts plant development and is
associated with heat-induced cytoplasmic foci. \emph{Journal of
Experimental Botany} \textbf{74}:2585--2602.
doi:\href{https://doi.org/10.1093/jxb/erad050}{10.1093/jxb/erad050}

\bibitem[\citeproctext]{ref-lohmann2001}
Lohmann JU, Hong RL, Hobe M, Busch MA, Parcy F, Simon R, Weigel D. 2001.
A Molecular Link between Stem Cell Regulation and Floral Patterning in
Arabidopsis. \emph{Cell} \textbf{105}:793--803.
doi:\href{https://doi.org/10.1016/s0092-8674(01)00384-1}{10.1016/s0092-8674(01)00384-1}

\bibitem[\citeproctext]{ref-Marinkovi2020}
Marinković M, Berger J, Jékely G. 2019. Neuronal coordination of motile
cilia in locomotion and feeding. \emph{Philosophical Transactions of the
Royal Society B: Biological Sciences} \textbf{375}:20190165.
doi:\href{https://doi.org/10.1098/rstb.2019.0165}{10.1098/rstb.2019.0165}

\bibitem[\citeproctext]{ref-ozpolat2021}
Ozpolat BD, Randel N, Williams EA, Bezares-Calderón LA, Andreatta G,
Balavoine G, Bertucci PY, Ferrier DEK, Gambi MC, Gazave E,
Handberg-Thorsager M, Hardege J, Hird C, Hsieh Y-W, Hui J, Mutemi KN,
Schneider SQ, Simakov O, Vergara HM, Vervoort M, Jékely G,
Tessmar-Raible K, Raible F, Arendt D. 2021. The Nereid on the rise:
\emph{Platynereis} as a model system. \emph{Zenodo}.
doi:\href{https://doi.org/10.5281/ZENODO.4907400}{10.5281/ZENODO.4907400}

\bibitem[\citeproctext]{ref-Saile2023}
Saile J, Wießner-Kroh T, Erbstein K, Obermüller DM, Pfeiffer A, Janocha
D, Lohmann J, Wachter A. 2023. SNF1-RELATED KINASE 1 and TARGET OF
RAPAMYCIN control light-responsive splicing events and developmental
characteristics in etiolated Arabidopsis seedlings. \emph{The Plant
Cell} \textbf{35}:3413--3428.
doi:\href{https://doi.org/10.1093/plcell/koad168}{10.1093/plcell/koad168}

\bibitem[\citeproctext]{ref-Wu2020}
Wu H, Qu X, Dong Z, Luo L, Shao C, Forner J, Lohmann JU, Su M, Xu M, Liu
X, Zhu L, Zeng J, Liu S, Tian Z, Zhao Z. 2020. WUSCHEL triggers innate
antiviral immunity in plant stem cells. \emph{Science}
\textbf{370}:227--231.
doi:\href{https://doi.org/10.1126/science.abb7360}{10.1126/science.abb7360}

\end{CSLReferences}

\end{document}

### 2024-06-06 manuscript/table_test.qmd
COS course day 2 updates

---
title: "table_test"
format: html
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Table

|   |   |   |   |   |
|---|---|---|---|---|
|   |   |   |   |   |
|   |   |   |   |   |
|   |   |   |   |   |

| Reagent type (species) or resource         | Designation                                        | Source or reference                                                                                | Identifiers          | Additional information                                                                                           |
|--------------------------------------------|----------------------------------------------------|----------------------------------------------------------------------------------------------------|----------------------|------------------------------------------------------------------------------------------------------------------|
|                                            |                                                    |                                                                                                    |                      |                                                                                                                  |
| biological sample (N. vectensis)           | larval, juvenile and adult N. vectensis            | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter           | N/A                  |                                                                                                                  |
| biological sample (cDNA)                   | cDNA obtained from N. vectensis                    | this study                                                                                         | N/A                  | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
| biological sample (peptide extract)        | peptide extracts obtained from N. vectensis        | this study                                                                                         | N/A                  | Peptides extracted from N. vectensis according to protocol explained in Material and Methods                     |
| genetic reagent (cDNA synthesis)           | SuperScript™ III First-Strand Synthesis System     | Invitrogen (from ThermoFisher)                                                                     | 18080051             |                                                                                                                  |
| genetic reagent (Polymerase)               | Q5® Hot Start High-Fidelity DNA Polymerase         | New England Biolabs                                                                                | M0493L               |                                                                                                                  |
| genetic reagent (DNA assembly)             | NEBuilder® HiFi DNA Assembly Master Mix            | New England Biolabs                                                                                | E2621L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | EcoRV restriction enzyme                           | New England Biolabs                                                                                | R3195L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | Afl2 restriction enzyme                            | New England Biolabs                                                                                | R0520L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | Hind3 restriction enzyme                           | New England Biolabs                                                                                | R3104L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | BamH1 restriction enzyme                           | New England Biolabs                                                                                | R3136L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | EcoRI restriction enzyme                           | New England Biolabs                                                                                | R3101L               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)                                        | Invitrogen (from ThermoFisher)                                                                     | V79020               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pRK5-Gqi9                                          | AddGene                                                                                            | 125711               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-G5A                                    | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-Gqi5/9                                 | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| recombinant DNA reagent                    | cloned N. vectensis GPCRs in pcDNA3.1(+)           | identified in this study                                                                           | N/A                  | full list of cloned GPCRs with sequences in Supplementary file 8                                                 |
| recombinant DNA reagent                    | synthesized N. vectensis GPCRs in pcDNA3.1(+)      | identified in this study, codon optimized and synthesized by GenScript                             | N/A                  | full list of synthesized GPCRs with original and codon optimized sequences in Supplementary file 8               |
| sequence-based reagent                     | cloning primers to create Gqi5/9                   | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| sequence-based reagent                     | GPCR cloning primers                               | this study                                                                                         | N/A                  | full list of primers with sequences in Supplementary file 8                                                      |
| peptide, recombinant protein               | custom peptides                                    | identified in this study, synthesized by GenScript                                                 | N/A                  | full list of peptides with sequences and purity in Supplementary file 2 and 3                                    |
| commercial assay or kit (PCR clean up)     | Monarch® PCR & DNA Cleanup Kit (5 μg)              | New England Biolabs                                                                                | T1030L               |                                                                                                                  |
| commercial assay or kit (Miniprep)         | GeneJET Plasmid Miniprep Kit                       | Thermo Fisher Scientific                                                                           | K0503                |                                                                                                                  |
| strain, strain background (E. coli, TOP10) | One Shot™ TOP10 Chemically Competent E. coli       | Thermo Fisher Scientific                                                                           | C404010              | E. coli strain used for general cloning                                                                          |
| cell line (HEK293)                         | HEK293 Cells expressing GFP-AEQUORIN in Cytoplasma | Angio-Proteomie                                                                                    | cAP-0200GFP-AEQ-Cyto |                                                                                                                  |
| chemical compound, drug                    | DMEM                                               | Gibco (from ThermoFisher)                                                                          | 10566016             |                                                                                                                  |
| chemical compound, drug                    | OptiMEM                                            | Gibco (from ThermoFisher)                                                                          | 11058021             |                                                                                                                  |
| chemical compound, drug                    | FBS                                                | Gibco (from ThermoFisher)                                                                          | 10500064             |                                                                                                                  |
| chemical compound, drug                    | PEI (Polyethylenimine, 25k Mw)                     | Sigma-Aldrich                                                                                      | 408727               | used 0.3 µl of a 1 mg/ml stock solution per 100 ng DNA                                                           |
| chemical compound, drug                    | Transfectamine 5000                                | AAT Bioquest                                                                                       | 60022                | used 0.3 µl per 100 ng of DNA                                                                                    |
| chemical compound, drug                    | Coelenterazine-h                                   | Promega                                                                                            | S2011                | diluted to 2 mM in Ethanol and used at a final concentration of 4 µM in the assays                               |
| chemical compound, drug                    | TRIzol™ Reagent                                    | Invitrogen (from ThermoFisher)                                                                     | 15596026             |                                                                                                                  |
| other                                      | Corning® 96 Well White Polystyrene Microplate      | Corning (from Sigma-Aldrich)                                                                       | CLS3903              | cell culture treated assay plates                                                                                |
| other                                      | Nunc™ EasYFlask™ T75 Cell Culture Flasks           | Nunc (from ThermoFisher)                                                                           | 156499               | cell culture flasks                                                                                              |
| other                                      | Flexstation 3 Multimode Microplate Reader          | Molecular Devices                                                                                  |                      | plate reader                                                                                                     |
| software, algorithm                        | SoftMax®  Pro 7                                    | Molecular Devices                                                                                  |                      |                                                                                                                  |
| software, algorithm                        | R                                                  | https://cran.rstudio.com/                                                                          |                      |                                                                                                                  |
| software, algorithm                        | RStudio                                            | https://posit.co/download/rstudio-desktop/                                                         |                      |                                                                                                                  |
| software, algorithm                        | SignalP4.1                                         | https://services.healthtech.dtu.dk/services/SignalP-6.0/                                           |                      |                                                                                                                  |
| software, algorithm                        | NeuroPID                                           | https://bio.tools/neuropid                                                                         |                      |                                                                                                                  |
| software, algorithm                        | HMMER3.1b2                                         | http://hmmer.org/download.html                                                                     |                      |                                                                                                                  |
| software, algorithm                        | CD-HIT                                             | https://sites.google.com/view/cd-hit                                                               |                      |                                                                                                                  |
| software, algorithm                        | TransDecoder                                       | https://github.com/TransDecoder/TransDecoder                                                       |                      |                                                                                                                  |
| software, algorithm                        | CLANS (desktop version)                            | https://mybiosoftware.com/clans-20101007-visualize-protein-families-based-pairwise-similarity.html |                      |                                                                                                                  |
| software, algorithm                        | CLANS (online toolkit)                             | https://toolkit.tuebingen.mpg.de/tools/clans                                                       |                      |                                                                                                                  |
| software, algorithm                        | Phobius                                            | https://phobius.sbc.su.se/data.html                                                                |                      |                                                                                                                  |
| software, algorithm                        | muscle alignment tool                              | https://drive5.com/muscle5/                                                                        |                      |                                                                                                                  |
| software, algorithm                        | MAFFT v7                                           | https://mafft.cbrc.jp/alignment/software/                                                          |                      |                                                                                                                  |
| software, algorithm                        | trimAl                                             | http://trimal.cgenomics.org/trimal                                                                 |                      |                                                                                                                  |
| software, algorithm                        | IQ-tree2                                           | http://www.iqtree.org/                                                                             |                      |                                                                                                                  |
| software, algorithm                        | Fasttree                                           | http://www.microbesonline.org/fasttree/                                                            |                      |                                                                                                                  |

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2024-06-06 presentation/RStudio_paper_writing_course_presentation_day2.qmd
COS course day 2 updates

---
title: "Rstudio in Data Science and Paper Writing - Day 2"
author: "Gáspár Jékely"
format:
  revealjs: 
    theme: [default, custom.scss]
    slide-number: false
    code-fold: false
    code-summary: "Code"
    chalkboard: 
      buttons: false
    preview-links: auto
scrollable: true
---

## Course program

::: columns
::: {.column width="50%"}
### Day 1

<br>

-   10:00-12:30 **Part 1** Why open science? Project management, data import, tidy data

-   12:30-13:30 lunch break

-   13:30-17:00 **Part 2**: Plotting, figure assembly
:::

::: {.column width="50%"}
### Day 2

<br>

- 9:30-12:30 **Part 3**: Manuscript writing, tables, references, data and figure embedding

- 12:30-13:30 lunch break

- 13:30-17:00 **Part 4**: GitHub, collaboration, sharing, version control

- 19:00 pub/dinner
:::
:::

```{r eval=TRUE, echo=FALSE}
source("../analysis/scripts/packages_and_functions.R")
```

## Paper writing in Quarto/Rmarkdown

-   Powerful and versatile text editing with simple Markdown syntax or visual editor (similar to Word)

-   Easy insertion and formatting of references from the web or a .bib file

-   Supports equations, tables, code blocks

-   Directly insert your figures generated by your scripts in the same project

-   Can 'knit' into html, pdf or docx formats

-   -\> Open manuscript/Manuscript.qmd\]

## Quarto - Documentation

<br>

-   Quarto enables you to weave together content and executable code into a finished presentation.
-   To learn more about Quarto presentations see <https://quarto.org/docs/presentations/>.

## The YAML header

- A YAML header contains YAML arguments, such as “title”, “author”, and “output”, demarcated by three dashes (-) on either end.
- When you create a new Quarto doc or presentation, it is created with a short YAML

```{r}
#| echo=TRUE, eval=FALSE
---
title: "Untitled"
format: html
---

```

- There is a more complex YAML in manuscript/Manuscript.qmd

```{r}
#| echo=TRUE, eval=FALSE

---
title: "New paper template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: default
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

```

## Inserting references

<br>

-   In Visual mode, go to 'Insert' -\> 'Citation'
-   search for reference on pubmed etc.
-   'Insert' will add the ref to the bibliograpy.bib file
-   in 'Source' mode, you can directly insert the reference with [@ref_id] (preferred, faster method)
-   add new refs to your .bib file with the command-line command:

:\$ curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.34550 \>\> ./references.bib <br>

::: callout-warning
-   need to add references.bib to the YAML header as bibliography: references.bib
-   also define bibliography style in the YAML with csl: elife.csl #add .csl according to journal
:::

## Tables

```{r}
#| echo=TRUE, eval=TRUE

#render built-in iris table with tinytable
tinytable::tt(head(iris))

#create some data
mydata <- tibble(
  gene = c("A", "B"),
  expression = c(1.1, 0.4)
  )

#render table
tt(mydata)

#read data
resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")

tt(
  resources_table, caption = "Key Resources Table", 
  theme = "grid", width = 1
  )

```

## Collaborative code and paper writing with Rstudio and GitHub

<br>

-   GitHub www.github.com is a platform for software development and version control
-   owned by Microsoft since 2018
-   developers can have public and private repositories
-   can share repositories privately with collaborators
-   integrates well with Rstudio
-   uses git protocol that is open source and also used by other code-hosting sites

## The workflow

-   Create a new project or clone a template project on GitHub
-   In Rstudio, New Project -\> Version control -\> add GitHub repo URL and save locally
-   Change the code
-   You can 'commit' and then 'push' changes to GitHub
-   Your collaborators can be added on GitHub
-   Collaborators can 'pull' to their own computer and 'push' their own changes
-   If two developers push changes to the same repo, this can lead to conflict
-   This can be managed by starting new 'branches'
-   Branches can be 'merged' to the original 'master' branch
-   A collaborator can issue a 'pull request' to merge their branch to the master

## Collaborations - sharing and commenting

<br>

-   Adding comments directly to the Quarto file with \<!--# my comment --> (these will not be knitted to the output)
- share as .docx and ask collaborators to use track changes (then why did we take this course...)
- collaborate on the same GitHub repository, use branches and pull requests (only makes sense if the collaborators are very involved)
- in principle you could use an Rproject for data, code and figures, and write text+refs on Gdocs+Paperpile or Overleaf+bib
- share commentable html through your github or other website
- we will use 'https://hypothes.is/' to add commenting functionality to an html 
- you need an account (easy and free)
- we use a https://github.com/hypothesis/client script that is sourced at the end of the quarto file by \<script src="hypothes.is/embed.js" async></script> to make this work

::: callout-warning
- you need to host the html on a website for sharing
:::

## Publication - GitHub and Zenodo integration

<br>

- GitHub is not a publishing platform 
- The owner could delete or make private the entire repo one day after publishing
- To stably publish your code and source data repository with a DOI ( globally unique and persistent identifier), you can use Zenodo
- Launched in 2013 by CERN
- Upload and link your GitHub repo to Zenodo

![](images/zenodo-gradient-1000.png){.absolute top="260" left="550" height="100"}

## Citation

<br>

- add/update a citation (CITATION.cff) file to your repo
- include the Zenodo DOI
- also cite your Zenodo repository in your manuscript
- see [example](https://zenodo.org/records/10978753)
- Make releases of your GitHub repo (e.g. initial submission, version of record), see [example](https://github.com/JekelyLab/Thiel_Yanez_Nematostella/tree/v3.0.0)
- The releases will be shown on Zenodo and are citeable

## Add README file to your repository

<br>

- open the README file (README.Rmd)
- README.md is generated from README.Rmd. Please edit that file
- modify the file according to your project
- add citation of the Zenodo repo with DOI
- add License, Acknowledgements etc.

### 2024-06-06 analysis/scripts/statistics_for_paper.R
add comment

@@ -42,4 +42,4 @@ Nanog_mean <- data_Ashwini_sel_M_SD %>%
   format(scientific = FALSE, big.mark = ",", digits = 3)
 Nanog_mean
 
-
+# we need more cool code here

### 2024-06-06 analysis/scripts/statistics_for_paper.R
more comments

@@ -30,6 +30,7 @@ data_Ashwini_sel <- data_Ashwini %>%
   select(1:6) %>%
   janitor::clean_names()
 
+# some interesting stuff here
 data_Ashwini_sel_M_SD <- data_Ashwini_sel %>%
   group_by(gene) %>%
   mutate(mean2dct = mean(x2_dct)) %>%

### 2024-06-06 manuscript/Manuscript.qmd
MS: abstract edit
more info about Platynereis
multiple manuscript edits

@@
 
+Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
+
 **text in bold** *italic* [underline]{.underline}
@@
 
-Test of git show.
+Test of git show. And another test.
 
@@
 
-*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]
+*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good campling location.
 
@@
 
-We would like to thank the Jekely lab for the R project template (<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by ...
+We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper.
+This work was funded by some funding agency.
+We would like to thank all the Platynereis that gave their lives for science.
 
@@
 library(tinytable)
+library(readxl)
 
-#read data
+# read data
 resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")
@@
 | d    |      |      |      |      |
+| v    | n    | f    |      | f    |
 

### 2024-11-01 presentation/RStudio_paper_writing_course_presentation_part1.qmd
R course: merge presentation, update sections

---
title: "Rstudio in Data Science and Paper Writing"
author: "Gáspár Jékely"
format:
  revealjs: 
    theme: [default, custom.scss]
    slide-number: false
    code-fold: false
    code-summary: "Code"
    chalkboard: 
      buttons: false
    preview-links: auto
scrollable: true
---

## Course program

<br>

- **Part 1**: Why open science? 
\

- **Part 2**: Project management, data import, tidy data
\

- **Part 3**: Plotting with ggplot
\

- **Part 4**: Assembly of figures
\

- **Part 5**: Manuscript writing, tables, references, data and figure embedding
\

- **Part 6**: GitHub, collaboration, sharing, version control

```{r eval=TRUE, echo=FALSE}
source("../analysis/scripts/packages_and_functions.R")
```

## Resources

<br><br>

- The [Tidyverse Cookbook](https://rstudio-education.github.io/tidyverse-cookbook/) (edited by Garrett Grolemund)\

https://rstudio-education.github.io/tidyverse-cookbook/

## Part 1 - Why do we need open science

- Reproducibility crisis
- Only a small fraction of research data is available
- An even smaller fraction of code is available (physicists are notoriously bad in sharing)
- Open access, if exists, is very expensive and maintains the profit of legacy publishers
- Scholarly literature is antiquated, dysfunctional and rewards prestige/hype over quality and integrity
- Scholarly workflows use non-professional, error-prone, closed-source software (MS, Adobe, Prism etc.) that makes sharing, integration, automation and collaboration difficult
- The final product of years of research is often only a single pdf file (1990s tech) behind a paywall
- Data, code and text are not searchable, reuseable, discoverable, shareable

## Most source data collected by scientists are not available

<br>

![](images/Data_publication_Pyramide.png){height=450}

## Most scientists use software developed for accounting

![](images/Scientists_rename_genes.png)
[theverge.com](https://www.theverge.com/2020/8/6/21355674/human-genes-rename-microsoft-excel-misreading-dates)

- the symbol MARCH1 has now become MARCHF1, while SEPT1 has become SEPTIN1, and so on

<br>

## Gene name errors are widespread in the scientific literature

<br><br>

![](images/13059_2016_1044_Fig1_HTML.webp)

::: aside
[Ziemann et al. (2016)](https://genomebiology.biomedcentral.com/articles/10.1186/s13059-016-1044-7)
:::

## Code is very often not shared or not shared stably

- *We assess the effectiveness of such a policy by (i) requesting data and code from authors and (ii) attempting replication of the published findings. We chose a random sample of 204 scientific papers published in the journal Science ... We found that we were able to obtain artifacts from 44% of our sample and were able to reproduce the findings for 26%.*

::: {.incremental}
- "When you approach a PI for the source codes and raw data, you better explain who you are, whom you work for, why you need the data and what you are going to do with it."

- "I have to say that this is a very unusual request without any explanation! Please ask your supervisor to send me an email with a detailed, and I mean detailed, explanation."

- "The data files remains our property and are not deposited for free access. Please, let me know the purpose you want to get the file and we will see how we can help you."

- "We do not typically share our internal data or code with people outside our collaboration."

:::

![](images/Stodden_PNAS.png){.absolute top="480" left="300" height="200"}

::: aside
[Stodden et al. (2018) ](https://doi.org/10.1073/pnas.1708290115)
:::

## Current state of scholarly digital infrastructure and knowhow

<img src=https://media1.tenor.com/images/f6362876996697b6a6f554b2ac3d3013/tenor.gif?itemid=10488408 width=200>

## What this course is about: what you can do to be open

- tools and approaches for transparent and open publishing
- a paper is not only text and figures, but also data and code
- all should be shared for reproducibility and openness
- otherwise it is not really 'published'
- we will use Rstudio to learn a comprehensive paper-writing pipeline
- code, tabulated data, figures, text, references, supplements all in one place
- collaborative working and sharing via GitHub (or other public repository)
- the figures are linked to their underlying data and code to generate them
- efficient version control
- faster, more transparent and reproducible workflow
- no software license is needed (no MS, no Adobe, no Matlab)
- once you master the approach I advocate, you don't want to go back...

## Part 2 - Packages, project management, data import, tidy data

<br>

- some rules on files, folders
- R projects
- installing and loading packages
- project templates
- importing various types of datasets
- principles of tidy data, tidying of messy datasets

## Go to GitHub and fork my repository

<br><br>

- do you have a GitHub account? 
- navigate to: https://github.com/JekelyLab/RStudio_paper_writing_course
- fork the repository to your GitHub (if you have an account already)
- go to RStudio -> New Project -> Git -> your repo's address (or my address)
- open /analysis/scripts/Course_exercises.R

## Rule nr. 1 -- relative working directories

<br>

```{r, eval=FALSE, echo=TRUE}
#| code-fold: false
getwd()
```

-   Never use absolute paths in your scripts, because they hinder sharing: no one else will have exactly the same directory configuration as you.

- Do not use setwd() to set your working dir

-   Keep all files associated with a project together — input data, R scripts, analytical results, figures. This is such a wise and common practice that RStudio has built-in support for this via **Rprojects**.

-   If you create a new Rproject, your working dir will in general be where you save the new project

-   Whenever you refer to a file with a relative path it will look for it in your wd.

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
list.files()
```

## Project management

<br>

* Use folders relative to your main .Rproject file (e.g. My_next_report.Rproject)

* Use a consistent directory structure to store code, data, text, figures, supplements, etc.

* Can be ensured if you always use the same project template

* We will use https://github.com/JekelyLab/RStudio_paper_writing_course

* Go to github and clone the project to your account ("Use this template")

* Go to RStudio -> new project -> version control -> git -> git URL of your new project

* select local dir and download the project with all directories to your computer

* let's check the project

* you can rename the .Rproject file to 'my favourite file name'

## Installing packages

* install the **tidyverse** package
```{r, eval=FALSE, echo=TRUE}
#| code-fold: false
install.packages("tidyverse")
```

- then load the package
```{r, eval=FALSE, echo=TRUE}
#| code-fold: false
library(tidyverse)
library(png)
```

## You can source packages and functions from one file

<br><br>

* open the R script analysis/scripts/Course_exercises.R with the example code

* source several packages and functions, listed in one file consistently across scripts

```{r eval=FALSE, echo=TRUE, tidy=FALSE, fig.height=5}
#| code-fold: false
source("../analysis/scripts/packages_and_functions.R")
```

## General good practice -- avoid spaces in file names

:::{.incremental}

<br>
```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
list.files("../analysis/data")
```

<br>
```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
readxl::read_excel("../analysis/data/data - José - March 2024.xlsx")
```
:::

## rio: A Swiss-Army Knife for Data I/O

- import xlsx, csv, tsv and many other formats with the same command

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
data_Jose <- rio::import("../analysis/data/data - José - March 2024.xlsx")
```

- export as csv

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
rio::export(data_Jose, "../analysis/data/data_Jose_March2024.csv")
```

- export as compressed csv

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
export(data_Jose, "../analysis/data/data_Jose_March2024.csv.zip")
```

- convert file formats

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false
rio::convert("../analysis/data/data - José - March 2024.xlsx",
"../analysis/data/data_Jose_March2024.csv")
```

::: aside
[Documentation of the rio package](http://gesistsa.github.io/rio/)
:::

## Save and share your computer environment and packages

```{r echo=TRUE, eval=TRUE}
#save session info and Rstudio version info for reproducibility
sessionInfo()
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```

## Read and preview data 1

```{r}
#| eval=TRUE, echo=TRUE
data_Jose <- readxl::read_excel("../analysis/data/data - José - March 2024.xlsx")
head(data_Jose)
glimpse(data_Jose)
str(data_Jose)
summary(data_Jose)
```

## Your workspace in R

- Recreate, rather than save workspace, save your coda and data, not workspace <br>

<img src=images/rstudio-workspace.png width=60%>

## Read and preview data 2

```{r}
#| eval=TRUE, echo=TRUE
data_Ashwini <- readxl::read_excel("../analysis/data/24_01_22qpcr_1 - ash pal.xlsx")
head(data_Ashwini)
glimpse(data_Ashwini)
str(data_Ashwini)
summary(data_Ashwini)
```

## Tidy data - definitions

from https://r4ds.hadley.nz/data-visualize

- A **variable** is a quantity, quality, or property that you can measure
- A **value** is the state of a variable when you measure it. The value of a variable may change from measurement to measurement.
- An **observation** is a set of measurements made under similar conditions (you usually make all of the measurements in an observation at the same time and on the same object). An observation will contain several values, each associated with a different variable. We’ll sometimes refer to an observation as a data point.

## Tidy data - definitions

* Tabular data is a set of values, each associated with a variable and an observation.

* Tabular data is tidy if each value is placed in its own “cell”, each variable in its own column, and each observation in its own row.

* “Tidy datasets are all alike, but every messy dataset is messy in its own way.” –– Hadley Wickham

__There are three interrelated rules which make a dataset tidy:__

* Each variable must have its own column.
* Each observation must have its own row.
* Each value must have its own cell.

<img src=images/tidy-1.png width=60%>

## Tidy data - an example tidy dataset

```{r, echo=TRUE}
knitr::kable(head(iris), format = 'html')
```

## Tibbles = tabular data in tidy format

```{r}
#| eval=FALSE, echo=TRUE
vignette("tibble")

```

- Tibbles are a modern take on data frames. 
- They keep the features that have stood the test of time, and drop the features that used to be convenient but are now frustrating.
- Tibbles encapsulate best practices for data frames.
- tibble() It never uses row.names().

## Tidy data -- __Why should I care?__

<br>

- after reading your data, you should always try to convert them into a tibble
- downstream analyses (plotting, mutating, sharing etc.) will be a lot easier
- data coming from other software, collaborators etc. are often 'messy'
- it is worth investing the time in tidying the data first
- sometimes it is tricky, as we will see...

## Let's try to fix a messy dataset...

```{r}
#| eval=TRUE, echo=TRUE
Gene <- c(rep("Nanog", 15), rep("oct4", 15), rep("sox2", 15),
  rep("Nestin", 15), rep("pax6", 15), rep("Foxg1", 15),
  rep("GAPDH", 15))
Gene

data_Ashwini$Gene <- Gene
head(data_Ashwini)
```

## Select only relevant columns and clean up names...

```{r}

#| eval=TRUE, echo=TRUE
data_Ashwini_sel <- data_Ashwini %>%
  select(1:6) %>%
  janitor::clean_names()
data_Ashwini_sel
```

## Add mean and SD columns with group_by() and mutate()

```{r}
#| eval=TRUE, echo=TRUE
data_Ashwini_sel_M_SD <- data_Ashwini_sel %>%
  group_by(gene) %>%
  mutate(mean2dct = mean(x2_dct)) %>%
  mutate(sd2dct = sd(x2_dct))
data_Ashwini_sel_M_SD
```

## Change data type...

```{r}
#| eval=TRUE, echo=TRUE
data_Ashwini_sel_M_SD <- data_Ashwini_sel_M_SD %>%
  mutate(ct_value = as.double(ct_value))
data_Ashwini_sel_M_SD
```

## Pivoting

- Tidying messy data is hard and requires parctice
- Read more here: https://r4ds.had.co.nz/tibbles.html

```{r}
#| eval=TRUE, echo=TRUE
data_Syn <- read_csv("../analysis/data/a-Syn-Data.csv")
data_Syn
# rename
data_Syn_clean <- data_Syn  %>%
  rename_with(~ gsub("_", "-", .x, fixed = TRUE)) %>%
  rename_with(~ gsub("...", "_", .x, fixed = TRUE))

tb_syn <- data_Syn_clean |>
  pivot_longer(matches("aSyn"), 
               names_to = c("condition", "sample"), 
               names_sep = "_",
               values_to = "fluorescence")
 tb_syn
```

## Part 3 - data plotting with ggplot

<br>

- once your data have been tidied up, plotting works like a charm
- use ggplot2 and a tibble as input
- ggplot2 is part of tidyverse and loads when you load tidyverse
- very versatile and extendable data visualisation package
- as input, you need a tibble (or a data.frame)
- supply data, define aesthetic mapping, add layers, define axes, plot theme etc.
- use the same theme (font size, line width etc.) across all figures in a project/paper/thesis
- statistical tests
- saving plots and source data

![](images/ggplot2-2177292224.png)

## Aesthetics, plot types and themes

* need to define 'aesthetics', which variable goes to x, y axes, to colour, size, line thickness etc.
* need to select plot type (geom_...  boxplot, line, points etc.)
* need to define 'theme' such as axis thickness, fonts, ticks, borders etc.

```{r eval = TRUE, echo = TRUE, fig.height = 4}

iris %>%  
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_boxplot(notch = TRUE) +
  theme_minimal()

```

## Resources

<br>
https://ggplot2.tidyverse.org/

https://r4ds.hadley.nz/

- ggplot cheat sheet
https://rstudio.github.io/cheatsheets/data-visualization.pdf

![](images/ggplot2-2177292224.png)

## Plot data - Jose

```{r}
#| eval=TRUE, echo=TRUE

plot_Jose1 <- data_Jose %>%
  ggplot(aes(x = genotype, y = length, fill = factor(Treatment, level=c('Control', 'ABA', 'Sulfate')), na.rm = TRUE)) +
  geom_boxplot() +
  theme_minimal() +
  scale_fill_manual(values = c("#D55E00", "#E69F00", "#cccccc")) +
  guides(fill = guide_legend(title = "Treatment"))

plot_Jose1

```

```{r, eval=TRUE, echo=TRUE}
#| code-fold: false

library(ggplot2)
plot_Jose2 <- data_Jose %>%
  ggplot(aes(x = genotype, y = length, fill = factor(Treatment, level=c('Control', 'ABA', 'Sulfate')), na.rm = TRUE)) +
  geom_violin() +
  geom_point( position=position_jitterdodge(jitter.width = 0.3, dodge.width = 0.9), alpha = 0.5, size = 0.4) +
  scale_fill_manual(values = c("#D55E00", "#E69F00", "#aaaaaa", "#dddddd")) +
  guides(fill = guide_legend(title = "Treatment")) 
plot_Jose2
```

## A note on languages

- you can also use python, bash etc in code blocks

```{python}
import matplotlib
print(matplotlib.__version__)
```

```{python, echo=TRUE}
#| label: fig-polar
#| fig-cap: "A line plot on a polar axis"

import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(
  subplot_kw = {'projection': 'polar'} 
)
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

## Plot data

```{r}
#| eval=TRUE, echo=TRUE
data_Ashwini_sel_M_SD %>%
  group_by(gene) %>%
  ggplot(aes(x = days, y = dt_ct, fill = gene )) +
  geom_boxplot()

data_Ashwini_sel_M_SD %>%
  ggplot(aes(x = ct_value)) +
  geom_histogram()

```
## Plot data

```{r}
#| eval=TRUE, echo=TRUE
plot_Ashwini_ct <- data_Ashwini_sel_M_SD %>%
  group_by(gene) %>%
  ggplot(aes(x = gene, y = ct_value, fill = gene )) +
  geom_boxplot(na.rm = TRUE) 
plot_Ashwini_ct

```

## Plot the Synuclein data

```{r eval = TRUE, echo = TRUE, fig.height = 5}
plot_syn <- tb_syn %>%
  ggplot(aes(x = Time, y = fluorescence, color = condition)) +
  geom_smooth(method = 'loess') +
  theme_minimal()
plot_syn

```

## Read and preview data 3

```{r}
#| eval=TRUE, echo=TRUE
data_Anchel <- readxl::read_excel("../analysis/data/240323 CIN Exp278 reporter assay - Anchel.xlsx")
head(data_Anchel)
glimpse(data_Anchel)
str(data_Anchel)
summary(data_Anchel)
```

## Save tidy data as source data for the plot/figure/paper

```{r}
#| echo=TRUE, eval=TRUE
write_csv2(data_Ashwini_sel_M_SD, "../manuscript/source_data/FigureX_Ashwini_source_data.csv")
# check
read_csv2("../manuscript/source_data/data_Ashwini_sel_M_SD.csv")
```

## Format plots with predefined complete ggplot2 themes

::: columns
::: {.column width=50%}
```{r}
#| echo=TRUE, eval=TRUE
plot_Jose1 +
  theme_dark()
plot_Jose1 +
  theme_bw()
plot_Jose1 +
  theme_linedraw()
```
:::
::: {.column width=50%}
```{r}
#| echo=TRUE, eval=TRUE
plot_Jose2 +
  theme_classic()
plot_Jose2 +
  theme_minimal()
plot_Jose2 +
  theme_light()
```
:::
:::

## Format plots with a common custom theme()

- Themes are a powerful way to customize the non-data components of your plots: i.e. titles, labels, fonts, background, gridlines, and legends.

```{r}
#| echo=TRUE, eval=TRUE
args(theme)
```

## Format plots with a common custom theme()

```{r}
#| echo=TRUE, eval=TRUE
theme_plots <- theme_minimal() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.key.size = unit(7, "mm")
  )

plot_Ashwini_ct <- plot_Ashwini_ct +
  theme_plots
plot_Ashwini_ct

plot_Jose1 <- plot_Jose1 +
  theme_plots
plot_Jose1

plot_Jose2 <- plot_Jose2 +
  theme_plots
plot_Jose2

plot_syn <- plot_syn +
  theme_plots
plot_syn
```

## Optional - save plots

```{r}
#| echo=TRUE, eval=TRUE
ggsave( "../analysis/pictures/plot_Jose1a.png",
  limitsize = FALSE,
  units = c("px"), plot_Jose1,
  width = 2400, height = 1400, bg = "white"
)

# save in a different size
ggsave( "../analysis/pictures/plot_Jose1b.png",
  limitsize = FALSE,
  units = c("px"), plot_Jose2,
  width = 2400, height = 2000, bg = "white"
)

ggsave(
  "../analysis/pictures/synuclein_plot.png", plot_syn, 
  bg = "white"
  )

```

## Part 4 - Assembly of figures with cowplot and patchwork

```{r}
#| echo=TRUE, eval=TRUE

img1 <- readPNG("../analysis/pictures/plot_Jose1a.png")
img2 <- readPNG("../analysis/pictures/plot_Jose1b.png")

panel_JoseA <- ggdraw() + draw_image(img1)
panel_JoseB <- ggdraw() + draw_image(img2)

#define layout with textual representation
layout <- "
AB
CD"

#assemble multipanel figure based on layout
Figure_Jose <- panel_JoseA + panel_JoseB + plot_Jose1 + plot_Jose2 +
  plot_layout(design = layout, heights = c(1, 1, 1, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png and pdf
ggsave("../manuscript/figures/Figure_Jose.png", limitsize = FALSE, 
       units = c("px"), Figure_Jose, width = 4000, height = 2000,
       bg = "white")

ggsave("../manuscript/figures/Figure_Jose.pdf", limitsize = FALSE, 
       units = c("px"), Figure_Jose, width = 3000, height = 1600)

image_read("../manuscript/figures/Figure_Jose.png")
```

## Annotating a ggplot object

```{r}
#| echo=TRUE, eval=TRUE

plot_syn_ann <- plot_syn +
  annotate("segment", x = 20, xend = 50, y = 1, yend = 1, linewidth = 1)+
  annotate("text", x = 34, y = 300, label = "30 sec", size = 3)
plot_syn_ann
```

## Annotating an image

```{r}
#| echo=TRUE, eval=TRUE

#read images
img_INNOS <- magick::image_read("../analysis/pictures/INNOS_synapses.png")

#define arrow endpoints 
arrow <- data.frame(x1 = 0.95, x2 = 0.95, y1 = 0.8, y2 = 0.9)

#add text labels
panel_INNOS <- ggdraw() + 
  draw_image(img_INNOS) +
  draw_label("INNOS", x = 0.3, y = 0.99, size = 10) +
  draw_label("NS plexus", x = 0.485, y = 0.59, size = 8) +
  draw_label("outgoing", x = 0.9, y = 0.45, size = 10, color='#E69F00') +
  draw_label("incoming", x = 0.89, y = 0.5, size = 10, color='#0072B2') +
  draw_label("D", x = 0.95, y = 0.93, size = 6) +
  draw_label("V", x = 0.95, y = 0.77, size = 6) +
  draw_label("*", x = 0.5, y = 0.29, color='black',size = 18,fontface='plain') +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrow, 
               arrow = arrow(ends = "both", type = "closed", length = unit(0.1,"cm")),
               lineend = "butt",
               linejoin = "mitre",
               arrow.fill = "black", size = 0.2)

#define layout
layout <- "AB"

#assemble multipanel figure based on layout
Figure_INNOS <- plot_syn_ann + panel_INNOS +
  plot_layout(design = layout, widths = c(2, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png
ggsave(
  "../manuscript/figures/Figure_INNOS.png", limitsize = FALSE,
  units = c("px"), Figure_INNOS, 
  width = 3000, height = 1000,
  bg = "white"
  )

#save figure as pdf
ggsave("../manuscript/figures/Figure_IHC.pdf", limitsize = FALSE, 
       units = c("px"), Figure_INNOS, width = 3000, height = 1000)

image_read("../manuscript/figures/Figure_IHC.png")
#img

```

## Adding consistent scale bars

- you could add the scale bar directly on the image e.g., in ImageJ, however..
- your scale bars may be misaligned and of varying thickness
- you can use cowplot::draw_line instead
- the x positions of the start and end of the line are defined as % of the panel width
- if you know the width of the image (e.g., can add it to file name), it is easy to calculate the size of the scale bar

```{r, eval=TRUE, echo=TRUE}
#| code-fold: true

#read images and make annotated panel
panel_NOS2d_HCR <- ggdraw() + draw_image(readPNG("../analysis/pictures/HCR-IHC_51_AP_NOS_actub_56um.png")) +
  draw_label("in situ HCR", x = 0.3, y = 0.99, size = 10) +
  draw_label("NOS", x = 0.12, y = 0.9, color="magenta", size = 11, fontface="italic") +
  draw_label("acTub", x = 0.36, y = 0.9, color="green", size = 11, fontface="plain") +
  draw_line(x = c(0.1, 0.46), y = c(0.08, 0.08), color = "white", size = 0.5) +
  draw_label(expression(paste("20 ", mu, " m")), x = 0.28, y = 0.11, color = "white", size = 8)

panel_NIT_HCR <- ggdraw() + draw_image(readPNG("../analysis/pictures/HCR_72_AP_NIT_94um.png")) +
  draw_label("transgene + IHC", x = 0.38, y = 0.99, size = 10) +
  draw_label("NOSp::palmi-3xHA", x = 0.34, y = 0.9, color="magenta", size = 10, fontface="plain") +
  draw_label("acTub", x = 0.8, y = 0.9, color="green", size = 10, fontface="plain") +
  draw_line(x = c(0.1, 0.31), y = c(0.08, 0.08), color = "white", size = 0.5) 
```

```{r}
#| echo=TRUE, eval=TRUE

#introduce gap in layout
layout <- "A#B"

#assemble multipanel figure based on layout
Figure_scalebars <- panel_NOS2d_HCR + panel_NIT_HCR +
  plot_layout(design = layout, widths = c(1, 0.03, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png
ggsave(
  "../manuscript/figures/Figure_scalebars.png",
  units = c("px"), Figure_scalebars, 
  width = 1700, height = 940, bg = "white"
  )

image_read("../manuscript/figures/Figure_scalebars.png")
image_read("../manuscript/figures/Figure_scalebars.png")
```

## Fine-tuning figure size and gaps

### Excercises

- save the figure in different sizes 
- introduce gap with # into layout, also need to define width of gap as say 0.05
- change position of scalebar and scalebar legend

```{r}
#| echo=TRUE, eval=TRUE

#no gap in layout
layout1 <- "AB"

#assemble multipanel figure based on layout
Figure_scalebars <- panel_NOS2d_HCR + panel_NIT_HCR +
  plot_layout(design = layout1, widths = c(1, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png
ggsave(
  "../manuscript/figures/Figure_scalebars_no_gap.png", 
  limitsize = FALSE,
  units = c("px"), Figure_scalebars, 
  width = 1700, height = 940,
  bg = "white"
  )

image_read("../manuscript/figures/Figure_scalebars_no_gap.png")

#introduce gap in layout
layout2 <- "A#B"

#assemble multipanel figure based on layout
Figure_scalebars <- panel_NOS2d_HCR + panel_NIT_HCR +
  plot_layout(design = layout2, widths = c(1, 0.03, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png
ggsave(
  "../manuscript/figures/Figure_scalebars_gap.png", 
  limitsize = FALSE,
  units = c("px"), Figure_scalebars, 
  width = 1700, height = 940,
  bg = "white"
  )

image_read("../manuscript/figures/Figure_scalebars_gap.png")

```

## More complex figure layouts

```{r}
#| echo=TRUE, eval=TRUE

#read images and make annotated panel
panel_Platy <- ggdraw() + draw_image(readPNG("../analysis/pictures/Platynereis_SEM_inverted_nolabel.png"))
panel_NOS <- ggdraw() + draw_image(readPNG("../analysis/pictures/HCR-IHC_51_AP_NOS_actub_56um.png"))
panel_FVRI <- ggdraw() + draw_image(readPNG("../analysis/pictures/FVRIa_rhoPhall_31h_200um.png"))
panel_Jose <- ggdraw() + draw_image(readPNG("../analysis/pictures/plot_Jose1b.png"))
panel_INNOS <- ggdraw() + draw_image(readPNG("../analysis/pictures/INNOS_synapses.png"))
panel_NIT <- ggdraw() + draw_image(readPNG("../analysis/pictures/IHC_55_AP_NITGC2_actub_61um.png"))
panel_DAF <- ggdraw() + draw_image(readPNG("../analysis/pictures/DAFFM.png"))
panel_model <- ggdraw() + draw_image(readPNG("../analysis/pictures/Magnitude_model_cPRC.png"))

#introduce gap in layout
layout <- "
AAAABBBBCCCC
AAAABBBBDDDD
############
EEEFFFGGGHHH
EEEFFFGGGHHH
"

#assemble multipanel figure based on layout
Figure_complex <- panel_Platy + panel_FVRI +  panel_NOS + 
  panel_NIT +
  panel_INNOS + panel_Jose + panel_DAF +
  panel_model +
  plot_layout(design = layout, heights = c(1, 1, 0.05, 1, 1)) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 12, face='plain'))

#save figure as png
ggsave(
  "../manuscript/figures/Figure_complex.png",
  units = c("px"), Figure_complex, 
  width = 2600, height = 1700, bg = "white"
  )

image_read("../manuscript/figures/Figure_complex.png")
```

## Vector graphics and drawings

<br>

- https://scidraw.io/ for high-quality CC-BY drawings
- Inkscape (free) or Illustrator (license) for vector graphics
- export as image, import into R workflow

## Image saved with a defined resolution (dpi)

```{r}
#| echo=TRUE, eval=TRUE

ggsave(
  "../manuscript/figures/Figure_complex_300dpi.png",
  units = c("cm"), Figure_complex, 
  width = 22, height = 13, dpi = 300, bg = "white"
  )
```

## Part 5 - Writing papers and reports in Quarto/Rmarkdown

-   Powerful and versatile text editing with simple Markdown syntax or visual editor (similar to Word)

-   Easy insertion and formatting of references from the web or a .bib file

-   Supports equations, tables, code blocks

-   Directly insert your figures generated by your scripts in the same project

-   Can 'knit' into html, pdf or docx formats

-   -\> Open manuscript/Manuscript.qmd\]

## Quarto - Documentation

<br>

-   Quarto enables you to weave together content and executable code into a finished presentation.
-   To learn more about Quarto presentations see <https://quarto.org/docs/presentations/>.

## The YAML header

- A YAML header contains YAML arguments, such as “title”, “author”, and “output”, demarcated by three dashes (-) on either end.
- When you create a new Quarto doc or presentation, it is created with a short YAML

```{r}
#| echo=TRUE, eval=FALSE
---
title: "Untitled"
format: html
---

```

- There is a more complex YAML in manuscript/Manuscript.qmd

```{r}
#| echo=TRUE, eval=FALSE

---
title: "New paper template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: default
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

```

## Inserting references

<br>

-   In Visual mode, go to 'Insert' -\> 'Citation'
-   search for reference on pubmed etc.
-   'Insert' will add the ref to the bibliograpy.bib file
-   in 'Source' mode, you can directly insert the reference with [@ref_id] (preferred, faster method)
-   add new refs to your .bib file with the command-line command:

:\$ curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.34550 \>\> ./references.bib <br>

::: callout-warning
-   need to add references.bib to the YAML header as bibliography: references.bib
-   also define bibliography style in the YAML with csl: elife.csl #add .csl according to journal
:::

## Tables

```{r}
#| echo=TRUE, eval=TRUE

#render built-in iris table with tinytable
tinytable::tt(head(iris))

#create some data
mydata <- tibble(
  gene = c("A", "B"),
  expression = c(1.1, 0.4)
  )

#render table
tt(mydata)

#read data
resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")

tt(
  resources_table, caption = "Key Resources Table", 
  theme = "grid", width = 1
  )

```

## Part 6 - Collaborative code and paper writing with Rstudio and GitHub

<br>

-   GitHub www.github.com is a platform for software development and version control
-   owned by Microsoft since 2018
-   developers can have public and private repositories
-   can share repositories privately with collaborators
-   integrates well with Rstudio
-   uses git protocol that is open source and also used by other code-hosting sites

## The workflow

-   Create a new project or clone a template project on GitHub
-   In Rstudio, New Project -\> Version control -\> add GitHub repo URL and save locally
-   Change the code
-   You can 'commit' and then 'push' changes to GitHub
-   Your collaborators can be added on GitHub
-   Collaborators can 'pull' to their own computer and 'push' their own changes
-   If two developers push changes to the same repo, this can lead to conflict
-   This can be managed by starting new 'branches'
-   Branches can be 'merged' to the original 'master' branch
-   A collaborator can issue a 'pull request' to merge their branch to the master

## Collaborations - sharing and commenting

<br>

-   Adding comments directly to the Quarto file with \<!--# my comment --> (these will not be knitted to the output)
- share as .docx and ask collaborators to use track changes (then why did we take this course...)
- collaborate on the same GitHub repository, use branches and pull requests (only makes sense if the collaborators are very involved)
- in principle you could use an Rproject for data, code and figures, and write text+refs on Gdocs+Paperpile or Overleaf+bib
- share commentable html through your github or other website
- we will use 'https://hypothes.is/' to add commenting functionality to an html 
- you need an account (easy and free)
- we use a https://github.com/hypothesis/client script that is sourced at the end of the quarto file by \<script src="hypothes.is/embed.js" async></script> to make this work

::: callout-warning
- you need to host the html on a website for sharing
:::

## Publication - GitHub and Zenodo integration

<br>

- GitHub is not a publishing platform 
- The owner could delete or make private the entire repo one day after publishing
- To stably publish your code and source data repository with a DOI ( globally unique and persistent identifier), you can use Zenodo
- Launched in 2013 by CERN
- Upload and link your GitHub repo to Zenodo

![](images/zenodo-gradient-1000.png){.absolute top="260" left="550" height="100"}

## Citation

<br>

- add/update a citation (CITATION.cff) file to your repo
- include the Zenodo DOI
- also cite your Zenodo repository in your manuscript
- see [example](https://zenodo.org/records/10978753)
- Make releases of your GitHub repo (e.g. initial submission, version of record), see [example](https://github.com/JekelyLab/Thiel_Yanez_Nematostella/tree/v3.0.0)
- The releases will be shown on Zenodo and are citeable

## Add README file to your repository

<br>

- open the README file (README.Rmd)
- README.md is generated from README.Rmd. Please edit that file
- modify the file according to your project
- add citation of the Zenodo repo with DOI
- add License, Acknowledgements etc.

### 2024-11-01 presentation/RStudio_paper_writing_course_presentation_part2.qmd
R course: merge presentation, update sections

---
title: "Rstudio in Data Science and Paper Writing"
subtitle: "Part 2"
author: "Gáspár Jékely"
format:
  revealjs: 
    theme: [default, custom.scss]
    slide-number: false
    code-fold: false
    code-summary: "Code"
    chalkboard: 
      buttons: false
    preview-links: auto
scrollable: true
---

## Course program

<br>
- **Section 1**: Why open science? Project management, data import, tidy data
- **Section 2**: Plotting, figure assembly
- **Section 3**: Manuscript writing, tables, references, data and figure embedding
- **Section 4**: GitHub, collaboration, sharing, version control

```{r eval=TRUE, echo=FALSE}
source("../analysis/scripts/packages_and_functions.R")
```

### 2024-11-01 analysis/scripts/Figure1.R

@@ -1,18 +1,18 @@
 # clean environment, source packages, colour palettes and functions ----------------
 source("analysis/scripts/packages_and_functions.R")
 
-#check working dir
+# check working dir
 here::here()
 
 # load the data -----------------------------------------------
 
-#read some pre-processed data text/csv file from the /data directory
+# read some pre-processed data text/csv file from the /data directory
 syn <- read_csv2("analysis/data/head_celltypes_syn_matrix.csv")
 syn
 
 # tidy the data ------------------
 syn_tb <- syn %>%
-  rename ("presyn_cell" = ...1) %>%
+  rename("presyn_cell" = ...1) %>%
   pivot_longer(-presyn_cell, names_to = "postsyn_cell", values_to = "synapses") %>%
   mutate(synapse_fraction = synapses / sum(synapses, na.rm = TRUE))
 
@@ -20,132 +20,160 @@ syn_tb
 
 # visualise the data and save plot ----------------------------------------
 
-#plot with ggplot
+# plot with ggplot
 syn_plot <- ggplot(syn_tb) +
-  geom_point(aes(x = postsyn_cell, y = presyn_cell, size = sqrt(synapses), color = synapse_fraction), 
-             stroke = 0,)+ 
+  geom_point(aes(x = postsyn_cell, y = presyn_cell, size = sqrt(synapses), color = synapse_fraction),
+    stroke = 0,
+  ) +
   theme(
-    axis.text.x = element_text (angle = 90,hjust = 1, vjust = 0.5, size=3), 
-    axis.text.y = element_text (angle = 0,hjust = 1, vjust = 0.5, size=3),
-    axis.title.x = element_text (size=14),
-    axis.title.y = element_text (size=14)
-  ) + 
-  labs(x="postsynaptic cell types",y="presynaptic cell types",title=" ") +
-  scale_size_area(max_size=1) +
-  guides(color = 'legend') +
+    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 3),
+    axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5, size = 3),
+    axis.title.x = element_text(size = 14),
+    axis.title.y = element_text(size = 14)
+  ) +
+  labs(x = "postsynaptic cell types", y = "presynaptic cell types", title = " ") +
+  scale_size_area(max_size = 1) +
+  guides(color = "legend") +
   scale_colour_gradient2(
     low = "#0072B2",
[…]

### 2024-11-01 analysis/scripts/packages_and_functions.R

@@ -19,7 +19,6 @@ library(magick)
 library(janitor)
 library(tinytable)
 library(rio)
-
 # define some colour-blind-friendly colour palettes --------------
 #From Color Universal Design (CUD): https://jfly.uni-koeln.de/color/
 Okabe_Ito <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", 

### 2024-11-02 manuscript/Manuscript.qmd
ms: test edits
talk update: split some slides, optimise layout, make presentation and course exercise same

@@
 ---
-title: "New paper template"
+title: "Paper or report template"
 subtitle: |
@@
 
-[This]{.underline} is an R **Markdown** *document.* ^Markdown^ is a simple formatting syntax for authoring HTML, PDF, and MS Word documents.
-For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+[This]{.underline} is a **Quarto** *document.* Quarto uses a simple ^Markdown^ formatting syntax for authoring HTML, PDF, and MS Word or .odt documents.
+For more details on using Quarto see <https://quarto.org/>.
 
 Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
-
-**text in bold** *italic* [underline]{.underline}
+Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.
 
@@
 
+*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good sampling location.
+
+# Results
+
+## Adding references
+
 You can add references either by referring to their id in the .bib file e.g., [@Marinkovi2020], or by switching to the visual editor (Cogwheel in the .Rmd menu -\> Use Visual Editor).
-[@Jokura_2023][@Jokura_2023][@Jacobs2023]
-
-It is now a test to edit the text and see how the changes show up on GitHub.
-
-Test of git show. And another test.
+[@Jokura_2023; @Jacobs2023]
 
 In the visual editor mode, go to 'Insert' -\> \@ Citation
-
 You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]
 
-The easiest way is to use the command line:
+One easy and techy way is to use the command line:
 
@@
 curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.91258.1 >> references.bib
+
+#make sure to use >> and not > otherwise you will overwrite your file!
 ```
 
-*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good campling location.
-
-The references are stored in manuscript/references.bib (need to be defined in the Yaml header).
+The references are stored in manuscript/references.bib (needs to be defined in the Yaml header).
 This file will automatically updated when you insert a new reference through the Visual editor \> Insert \> Citations.
 
-[@ozpolat2021][@Wu2020; @Saile2023; @Lohmann2023][@lohmann2001]
+[@ozpolat2021; @Wu2020; @Saile2023; @Lohmann2023; @lohmann2001]
 
@@
 
-## Results
+Now edit the text, add a few references and press -> Render and see how the changes show up on the rendered document.
+It is easier and faster to render your document to html.
+You will get a very nice dynamic layout that you can read in the browser (use Firefox).
+You can also render into pdf, but you need to install a version of latex for that.
+An easy alternative to generate a nice pdf is to open the html version in a browser (in this case Chrome gives the best results) and print to a pdf file.
 
-Inserting Figures <!--# I don't agree here -->
-
-Test comment here. <!--# Hi -->
+## Inserting figures
 
@@
 We use knitr::include_graphics for this.
-The title and legend can also be edited, as will as the width of the output figure.
-Test comment behaviour: <!--# Test comment for git show -->
+The title and legend can also be edited, as well as the width of the output figure.
 
@@
 
-## Equations
+## Adding equations
 
@@
 
-## Acknowledgements
+## Inserting comments
+
+Inserting comments: <!--# I don't agree here -->
+You can also use the visual editor and insert -> comment.
+
+Test comment here. <!--# Hi -->
+
+# Acknowledgements
 
 We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper.
-This work was funded by some funding agency.
-We would like to thank all the Platynereis that gave their lives for science.
+This work was funded by xy funding agency.
 
-## Materials and Methods
+# Materials and Methods
 
@@
 
-## References
+# References
 

### 2024-11-02 manuscript/Manuscript.tex
talk update: split some slides, optimise layout, make presentation and course exercise same

@@
 \UseTblrLibrary{booktabs}
+\UseTblrLibrary{rotating}
 \UseTblrLibrary{siunitx}
@@
 \hypersetup{
-  pdftitle={New paper template},
+  pdftitle={Paper or report template},
   colorlinks=true,
@@
 
-\title{New paper template}
+\title{Paper or report template}
 \usepackage{etoolbox}
@@
 
-\ul{This} is an R \textbf{Markdown} \emph{document.}
-\textsuperscript{Markdown} is a simple formatting syntax for authoring
-HTML, PDF, and MS Word documents. For more details on using R Markdown
-see \url{http://rmarkdown.rstudio.com}.
+\ul{This} is a \textbf{Quarto} \emph{document.} Quarto uses a simple
+\textsuperscript{Markdown} formatting syntax for authoring HTML, PDF,
+and MS Word or .odt documents. For more details on using Quarto see
+\url{https://quarto.org/}.
 
-\textbf{text in bold} \emph{italic} \ul{underline}
+Here is our abstract. We discovered that medaka fish can eat
+Arabidpopsis shoop apical meristeme cells to regulate energy metabolism
+(data not shown). Here is some \textbf{text in bold} \emph{italic}
+\ul{underline} and \textsuperscript{superscript}.
 
@@
 
+\emph{Platynereis dumerilii} is a marine annelid\ldots{} (Ozpolat et
+al., 2021). It is also the coolest model organism. It lives in shallow
+sea on seagrass. Ischia is a good sampling location.
+
+\section{Results}\label{results}
+
+\subsection{Adding references}\label{adding-references}
+
 You can add references either by referring to their id in the .bib file
 e.g., (Marinković et al., 2019), or by switching to the visual editor
-(Cogwheel in the .Rmd menu -\textgreater{} Use Visual Editor). {[}Jokura
-et al. (2023){]}(Jokura et al., 2023)(Jacobs and Ryu, 2023)
+(Cogwheel in the .Rmd menu -\textgreater{} Use Visual Editor). (Jacobs
+and Ryu, 2023; Jokura et al., 2023)
 
-It is now a test to edit the text and see how the changes show up on
-GitHub.
-
-Test of git show.
-
-In the visual editor mode, go to `Insert' -\textgreater{} @ Citation
-
-You can select a Zotero library, PubMed, CrossRef etc. and insert the
+In the visual editor mode, go to `Insert' -\textgreater{} @ Citation You
+can select a Zotero library, PubMed, CrossRef etc. and insert the
 citations. (Jacobs and Ryu, 2023)
 
-The easiest way is to use the command line:
+One easy and techy way is to use the command line:
 
@@
 \ExtensionTok{curl} \AttributeTok{{-}LH} \StringTok{"Accept: application/x{-}bibtex"}\NormalTok{ https://doi.org/10.7554/eLife.91258.1 }\OperatorTok{\textgreater{}\textgreater{}}\NormalTok{ references.bib}
+
+\CommentTok{\#make sure to use \textgreater{}\textgreater{} and not \textgreater{} otherwise you will overwrite your file!}
 \end{Highlighting}
 \end{Shaded}
-
-\emph{Platynereis dumerilii} is a marine annelid\ldots{} (Ozpolat et
-al., 2021)
 
@@
 
-{[}Ozpolat et al. (2021){]}(Lohmann et al., 2023; Saile et al., 2023; Wu
-et al., 2020)(Lohmann et al., 2001)
+(Lohmann et al., 2023; Lohmann et al., 2001; Ozpolat et al., 2021; Saile
+et al., 2023; Wu et al., 2020)
 
@@
 
-\subsection{Results}\label{results}
+Now edit the text, add a few references and press -\textgreater{} Render
+and see how the changes show up on the rendered document. It is easier
+and faster to render your document to html. You will get a very nice
+dynamic layout that you can read in the browser (use Firefox). You can
+also render into pdf, but you need to install a version of latex for
+that. An easy alternative to generate a nice pdf is to open the html
+version in a browser (in this case Chrome gives the best results) and
+print to a pdf file.
 
-Inserting Figures
-
-Test comment here.
+\subsection{Inserting figures}\label{inserting-figures}
 
@@
 
-\subsection{Equations}\label{equations}
+\subsection{Adding equations}\label{adding-equations}
 
@@
 
-\subsection{Acknowledgements}\label{acknowledgements}
+\subsection{Inserting comments}\label{inserting-comments}
 
-We would like to thank the Jekely lab for the R project template
-(\url{https://github.com/JekelyLab/new_paper_template}) we used to write
-this paper. This work was funded by \ldots{}
+Inserting comments: You can also use the visual editor and insert
+-\textgreater{} comment.
 
-\subsection{Materials and Methods}\label{materials-and-methods}
+Test comment here.
+
+\section{Acknowledgements}\label{acknowledgements}
+
+We would like to thank the \href{https://github.com/JekelyLab}{Jekely
+lab} for the \href{https://github.com/JekelyLab/new_paper_template}{R
+project template} we used to write this paper. This work was funded by
+xy funding agency.
+
+\section{Materials and Methods}\label{materials-and-methods}
 
@@
 d & & & & \\
+v & n & f & & f \\
 \end{longtable}
@@
 
-\subsection{References}\label{references}
+\section{References}\label{references}
 

### 2024-11-02 presentation/RStudio_paper_writing_course_presentation_part1.qmd
talk update: split some slides, optimise layout, make presentation and course exercise same

@@
 title: "Rstudio in Data Science and Paper Writing"
-author: "Gáspár Jékely"
+author: "Gáspár Jékely <br> Centre for Organismal Studies, Heidelberg University"
 format:
@@
 
-<img src=https://media1.tenor.com/images/f6362876996697b6a6f554b2ac3d3013/tenor.gif?itemid=10488408 width=200>
+<img src=https://media1.tenor.com/images/f6362876996697b6a6f554b2ac3d3013/tenor.gif?itemid=10488408 width=160>
 
@@
 - go to RStudio -> New Project -> Git -> your repo's address (or my address)
+- select local dir and download the project with all directories to your computer
+- let's check the project
+- you can rename the .Rproject file to 'my favourite file name'
 - open /analysis/scripts/Course_exercises.R
@@
 
+## Use R projects (.Rproj)
+
+<br>
+
 -   Keep all files associated with a project together — input data, R scripts, analytical results, figures.
@@
 
--   Whenever you refer to a file with a relative path it will look for it in your wd.
+-   Whenever you refer to a file with a relative path it will look for it in your working dir.
+
+- in case you used setwd() in a script (you should not) you can find your Rproject directory with here()
+
+```{r, eval=TRUE, echo=TRUE}
+here::here()
+
+#test, but you should not do this
+setwd("~")
+getwd()
+
+#get back to Rproj dir
+setwd(here::here())
+getwd()
+# all good again
+```
+
+## Use R projects (.Rproj)
+
+<br>
+
+- list files in your working dir
 
@@
 
-<br>
+<br><br><br>
 
@@
 
-* We will use https://github.com/JekelyLab/RStudio_paper_writing_course
-
-* Go to github and clone the project to your account ("Use this template")
-
-* Go to RStudio -> new project -> version control -> git -> git URL of your new project
-
-* select local dir and download the project with all directories to your computer
-
-* let's check the project
-
-* you can rename the .Rproject file to 'my favourite file name'
+* Check the folder structure in the downloaded project template
 
@@
 
-## rio: A Swiss-Army Knife for Data I/O
+## Save and share your computer environment and packages
+
+```{r echo=TRUE, eval=TRUE}
+#save session info and Rstudio version info for reproducibility
+sessionInfo()
+writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
+```
+
+## File import and saving -- rio: A Swiss-Army Knife for Data I/O
 
@@
 :::
-
-## Save and share your computer environment and packages
-
-```{r echo=TRUE, eval=TRUE}
-#save session info and Rstudio version info for reproducibility
-sessionInfo()
-writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
-```
 
@@
 
-- once your data have been tidied up, plotting works like a charm
+- once your data have been tidied up, plotting is a lot easier
 - use ggplot2 and a tibble as input
@@
 
+## Faceting
+
+<br>
+
+- Faceting means spreading the data across different panels
+
+- Need to define 'facets', a set of variables or expressions quoted by vars() defining faceting groups
+
+```{r eval = TRUE, echo = TRUE, fig.height = 4}
+iris %>%  
+  ggplot(aes(
+    x = Petal.Length, y = Sepal.Width, 
+    color = Species, size = Sepal.Width, shape = Species) 
+    ) +
+  geom_point(alpha = 0.5) +
+  facet_wrap(vars(Species))
+```
+
 ## Resources
@@
 
-```{python}
+```{python, echo=TRUE}
 import matplotlib
@@
 summary(data_Anchel)
+```
+
+# Add significance values of stats
+
+```{r}
+#| eval=TRUE, echo=TRUE
+
+plot_Ashwini_ct +
+  stat_compare_means(
+    aes(label = after_stat(p.format)),
+    method = "wilcox.test",
+    #ref.group = "Foxg1"
+    comparisons = list( c("GAPDH", "Nanog"), c("GAPDH", "oct4"), c("GAPDH", "pax6") )
+    )
 ```
@@
 img2 <- readPNG("../analysis/pictures/plot_Jose1b.png")
-
 panel_JoseA <- ggdraw() + draw_image(img1)
@@
 #save figure as png and pdf
-ggsave("../manuscript/figures/Figure_Jose.png", limitsize = FALSE, 
-       units = c("px"), Figure_Jose, width = 4000, height = 2000,
-       bg = "white")
-
-ggsave("../manuscript/figures/Figure_Jose.pdf", limitsize = FALSE, 
-       units = c("px"), Figure_Jose, width = 3000, height = 1600)
+ggsave(
+  "../manuscript/figures/Figure_Jose.png", limitsize = FALSE, 
+  units = c("px"), Figure_Jose, width = 4000, height = 2000, bg = "white"
+  )
+ggsave(
+  "../manuscript/figures/Figure_Jose.pdf", limitsize = FALSE, 
+  units = c("px"), Figure_Jose, width = 3000, height = 1600
+  )
+```
+
+```{r}
+#| echo=FALSE, eval=TRUE
 
@@
                arrow.fill = "black", size = 0.2)
-
+```
+
+## Annotating an image
+
+```{r}
+#| echo=TRUE, eval=TRUE
 #define layout
@@
 #save figure as pdf
-ggsave("../manuscript/figures/Figure_IHC.pdf", limitsize = FALSE, 
-       units = c("px"), Figure_INNOS, width = 3000, height = 1000)
+ggsave(
+  "../manuscript/figures/Figure_IHC.pdf", limitsize = FALSE, 
+  units = c("px"), Figure_INNOS, width = 3000, height = 1000
+  )
+```
+
+```{r}
+#| echo=FALSE, eval=TRUE
 
 image_read("../manuscript/figures/Figure_IHC.png")
-#img
-
 ```
@@
 
+## Reading tif files, parsing metadata like image scale
+
+```{r}
+#| echo=TRUE, eval=TRUE
+#| 
+img_tif <- magick::image_read("../analysis/pictures/INNOS_synapses.tif")
+img_scale <- image_info(img_tif)$width/as.numeric(str_split(image_info(img_tif)$density, "x")[[1]][1])
+img_scale #not precise
+
+# alternatively use ijtiff
+library(ijtiff)
+img_tif_ij <- ijtiff::read_tags("../analysis/pictures/INNOS_synapses.tif")
+img_scale <- img_tif_ij$frame1$width/img_tif_ij$frame1$x_resolution
+img_scale
+
+panel_INNOS_tif <- ggdraw() + draw_image(img_tif)
+
+Figure_INNOS_with_tif <- plot_syn_ann + panel_INNOS_tif +
+  plot_layout(design = layout, widths = c(2, 1)) +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 12, face='plain'))
+
+#save figure as png
+ggsave(
+  "../manuscript/figures/Figure_INNOS_with_tif.png", limitsize = FALSE,
+  units = c("px"), Figure_INNOS_with_tif, 
+  width = 3000, height = 1000, bg = "white"
+  )
+```
+
+```{r}
+#| echo=FALSE, eval=TRUE
+
+image_read("../manuscript/figures/Figure_INNOS_with_tif.png")
+```
+
 ## Fine-tuning figure size and gaps
 
-### Excercises
+### Exercises
 
@@
 "
+```
+
+## More complex figure layouts
+
+```{r}
+#| echo=TRUE, eval=TRUE
 
@@
   )
-
+```
+
+```{r}
+#| echo=FALSE, eval=TRUE
 image_read("../manuscript/figures/Figure_complex.png")
@@
 
--   -\> Open manuscript/Manuscript.qmd\]
+-   -\> Open manuscript/Manuscript.qmd
 
@@
 format:
-  html: default
+  html: 
+    embed-resources: true
   pdf:
@@
 
+## Simple syntax
+
+- [This is]{.underline} 
+- A **Quarto** *document.* 
+- Quarto uses a simple ^Markdown^ formatting syntax for authoring HTML, PDF, and MS Word or .odt documents. - Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.
+
 ## Inserting references
@@
 -   search for reference on pubmed etc.
--   'Insert' will add the ref to the bibliograpy.bib file
+-   'Insert' will add the ref to themanuscript/ bibliograpy.bib file (needs to be defined in the Yaml header)
+-   in our doc, references will be formatted in the eLife style (defined in the Yaml header under: csl: elife.csl)
+-   The elife.csl file is saved in the manuscript folder.
+-   For a different format, download the respective .csl file (e.g., from the Zotero style repository <https://www.zotero.org/styles>)
 -   in 'Source' mode, you can directly insert the reference with [@ref_id] (preferred, faster method)
--   add new refs to your .bib file with the command-line command:
+
+## Inserting references
+
+<br>
+
+-   you can also add new refs to your .bib file with the command-line command:
 
@@
 -   also define bibliography style in the YAML with csl: elife.csl #add .csl according to journal
+- if you use the command line, use >> and not > otherwise you will overwrite your file!
 :::
+
+## Inserting figures
+
+<br>
+
+-   we can now insert the figures we generated previously and saved under /manuscript/figures or /manuscript/figure_supplements
+
+-   Figure title and legend can also be edited, as well as width
+
+```{r, out.width = "100%", fig.cap="**Figure 1. A figure** (A) A nice picture. (B) legend.  (C) <br> (D) " }
+#| echo: true
+
+knitr::include_graphics("../manuscript/figures/Figure1.png")
+```
+
+## Adding equations
+
+<br>
+
+- Equations can also be inserted, Insert -\> Display Math:
+
+$$
+\bar{X} = \frac{\sum_{i=1}^{n} x_{i}}{n}
+$$
+## Sourcing code and working with variable
+
+```{r}
+#| eval: true
+source("../analysis/scripts/statistics_for_paper.R")
+```
+
+-   We can use the 'r variable' syntax to add variables calculated in the sourced code directly to the text
+-   This way if the underlying dataset changes, we just reprocess a calculation and insert the result directly into our manuscript
+- the script is sourced and it runs but the output is not included in the knitted output.
+But we can access the variables defined in the sourced script simply by adding \` r var_name \` between \` backticks, in this case max_PRC value is `r max_PRC` (now this number comes from our sourced script).
 

### 2024-11-02 analysis/scripts/Course_exercises.R

@@ -1,13 +1,7 @@
 # RStudio paper writing course - excercises
 # Gaspar Jekely, 2024
 
-# sourcing, installing and loading packages -------------------------------
-
-# installing packages
-install.packages("tidyverse")
-
-# source multiple packages from one file
-source("analysis/scripts/packages_and_functions.R")
+# working directory, sourcing, installing and loading packages -------------------------------
 
 #check your working dir (should be the .rproject dir)
 getwd()
@@ -24,12 +18,18 @@ setwd(here::here())
 getwd()
 # all good again
 
+#listing files in your working directory
 list.files()
+
+# installing packages
+install.packages("tidyverse")
 
 #loading packages
 library(tidyverse)
 library(png)
 
+# source multiple packages from one file
+source("analysis/scripts/packages_and_functions.R")
 
 # share session info ------------------------------------------------------
 
@@ -44,13 +44,6 @@ data_Jose <- readxl::read_excel("analysis/data/data - José - March 2024.xlsx")
 # alternatively, use the rio package with import() to automatically recognise format and import
 data_Jose <- rio::import("analysis/data/data - José - March 2024.xlsx")
 
-View(data_Jose)
-head(data_Jose)
-glimpse(data_Jose)
-str(data_Jose)
-summary(data_Jose)
-data_Jose
-
 
 # rio: A Swiss-Army Knife for Data I/O  -----------------------------------
 
@@ -61,8 +54,22 @@ export(data_Jose, "analysis/data/data_Jose_March2024.csv.zip")
 
 #convert file formats
 rio::convert("analysis/data/data - José - March 2024.xlsx",
-"analysis/data/data_Jose_March2024.csv")
+             "analysis/data/data_Jose_March2024.csv")
 
+
+# preview data ------------------------------
+
+View(data_Jose)
+head(data_Jose)
+glimpse(data_Jose)
+str(data_Jose)
+summary(data_Jose)
+data_Jose
+
+# check your workspace settings, do not save workspace -------------
+
+# go in the menu to Tools -> Global options 
+#untick Restore .Rdata into workspace at startup
 
[…]

### 2024-11-04 presentation/RStudio_paper_writing_course_presentation.qmd
Del part2: fused to part 1, add test slide transition

--- 2024-11-02 presentation/RStudio_paper_writing_course_presentation_part1.qmd
@@
     theme: [default, custom.scss]
-    slide-number: false
+    slide-number: true
     code-fold: false
@@
 
-## Most scientists use software developed for accounting
+## Most scientists use software developed for accounting {transition="fade" transition-speed="fast"}
 

### 2024-11-11 manuscript/Manuscript.qmd
MS, presentation: edits, update git slide

@@
   fig-title: Figure     # (default is "Figure")
-max-width: 100%
 format:
@@
 bibliography: references.bib #add bibliography in this file
-csl: elife.csl #change according to journal
+csl: development.csl #change according to journal
 ---
@@
 
-Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
+Here is our **abstract**.
+We *discovered* that `medaka` fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
 Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.
 
-# Introduction
+## Introduction
+
+## Sub-intro
+
+### Sub-sub-intr
+
+###### sub-sub-sub-intro
+
+##### sub-sub-sub-sub-intro
 
@@
 
+it is just like ms word, let's add a reference [@lyndby2023; @Pavlov2006] another one [@Marino2004; @Pavlov2006] [@Saile2023; @ozpolat2021]
+
 # Results
+
+Histology of the crocodile [@myburgh2023]
 
@@
 
-In the visual editor mode, go to 'Insert' -\> \@ Citation
-You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]
+In the visual editor mode, go to 'Insert' -\> \@ Citation You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]
+
+Nile croc paper [@pooley1976nile]
 
@@
 
-Now edit the text, add a few references and press -> Render and see how the changes show up on the rendered document.
+Now edit the text, add a few references and press -\> Render and see how the changes show up on the rendered document.
 It is easier and faster to render your document to html.
@@
 
-knitr::include_graphics("figures/Figure_complex.png")
+knitr::include_graphics("figures/Figure_scalebars_gap.png")
 ```
@@
 
-Inserting comments: <!--# I don't agree here -->
-You can also use the visual editor and insert -> comment.
+Inserting comments: <!--# I don't agree here --> You can also use the visual editor and insert -\> comment.
 
@@
 
-We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper.
+We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](https://github.com/JekelyLab/new_paper_template) we used to write this paper.
 This work was funded by xy funding agency.
@@
 |---------------|---------------|---------------|---------------|---------------|
-| biological sample (N.
-vectensis)     | larval, juvenile and adult N.
-vectensis        | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter | N/A         | NA                                                                                                               |
-| biological sample (cDNA)             | cDNA obtained from N.
-vectensis                | this study                                                                               | N/A         | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
-| biological sample (peptide extract)  | peptide extracts obtained from N.
-vectensis    | this study                                                                               | N/A         | Peptides extracted from N.
-vectensis according to protocol explained in Material and Methods                     |
+| biological sample (N. vectensis) | larval, juvenile and adult N. vectensis | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter | N/A | NA |
+| biological sample (cDNA) | cDNA obtained from N. vectensis | this study | N/A | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
+| biological sample (peptide extract) | peptide extracts obtained from N. vectensis | this study | N/A | Peptides extracted from N. vectensis according to protocol explained in Material and Methods |
 | genetic reagent (cDNA synthesis) | SuperScript™ III First-Strand Synthesis System | Invitrogen (from ThermoFisher) | 18080051 | NA |
@@
 
+## A table from tablesgenerator
+
+| gene   | days | raw_data | ct_value | dt_ct              | x2_dct               | mean2dct             | sd2dct               |
+|--------|------|----------|----------|--------------------|----------------------|----------------------|----------------------|
+| Nanog  | d0   | J1       | 22,491   | 6,956000000000000  | 0,008054439990584290 | 0,080889155034072582 | 9,40847959654144e-02 |
+| Nanog  | d0   | J2       | 19,877   | 4,395999999999999  | 0,047497651762547402 | 0,080889155034072582 | 9,40847959654144e-02 |
+| Nanog  | d0   | J3       | 19,164   | 2,418000000000003  | 0,187115373349086067 | 0,080889155034072582 | 9,40847959654144e-02 |
+| Nanog  | d7   | J4       | 21,177   | 4,667999999999999  | 0,039336161672026825 | 0,031927117712361432 | 7,83151167074938e-03 |
+| Nanog  | d7   | J5       | 21,812   | 4,934000000000001  | 0,032712821311705470 | 0,031927117712361432 | 7,83151167074938e-03 |
+| Nanog  | d7   | J6       | 22,303   | 5,397000000000002  | 0,023732370153351993 | 0,031927117712361432 | 7,83151167074938e-03 |
+| Nanog  | d11  | J7       | 22,930   | 7,436000000000000  | 0,005774853247163445 | 0,145298820021575043 | 2,41582234272199e-01 |
+| Nanog  | d11  | J8       | 22,915   | 7,412999999999998  | 0,005867655964613011 | 0,145298820021575043 | 2,41582234272199e-01 |
+| Nanog  | d11  | J9       | 17,831   | 1,236999999999998  | 0,424253950852948647 | 0,145298820021575043 | 2,41582234272199e-01 |
+| Nanog  | d15  | J10      | 15,848   | 1,252000000000001  | 0,419865746472069978 | 0,159625405875477383 | 2,25708832493508e-01 |
+| Nanog  | d15  | J11      | 20,295   | 4,581000000000001  | 0,041781265481410403 | 0,159625405875477383 | 2,25708832493508e-01 |
+| Nanog  | d15  | J12      | 20,492   | 5,859000000000002  | 0,017229205672951744 | 0,159625405875477383 | 2,25708832493508e-01 |
+| Nanog  | d16  | J13      | 21,168   | 5,347999999999999  | 0,024552266145861899 | 0,036597442578737135 | 1,04525811603947e-02 |
+| Nanog  | d16  | J14      | 20,984   | 4,575000000000003  | 0,041955390711883152 | 0,036597442578737135 | 1,04525811603947e-02 |
+| Nanog  | d16  | J15      | 20,974   | 4,530000000000001  | 0,043284670878466366 | 0,036597442578737135 | 1,04525811603947e-02 |
+| oct4   | d0   | K1       | 17,910   | 2,375000000000000  | 0,192776353175992593 | 0,311031348034201960 | 1,83714182145261e-01 |
+| oct4   | d0   | K2       | 17,681   | 2,200000000000001  | 0,217637640824030865 | 0,311031348034201960 | 1,83714182145261e-01 |
+| oct4   | d0   | K3       | 17,682   | 0,936000000000000  | 0,522680050102582450 | 0,311031348034201960 | 1,83714182145261e-01 |
+| oct4   | d7   | K4       | 21,113   | 4,603999999999999  | 0,041120453907156532 | 0,049755310269836310 | 1,48819426940308e-02 |
+| oct4   | d7   | K5       | 21,479   | 4,600999999999999  | 0,041206050452886472 | 0,049755310269836310 | 1,48819426940308e-02 |
+| oct4   | d7   | K6       | 20,807   | 3,901000000000000  | 0,066939426449465933 | 0,049755310269836310 | 1,48819426940308e-02 |
+| oct4   | d11  | K7       | 19,617   | 4,123000000000001  | 0,057392260143807688 | 0,090862010483616931 | 4,52910618365094e-02 |
+| oct4   | d11  | K8       | 19,282   | 3,779999999999999  | 0,072795849154278516 | 0,090862010483616931 | 4,52910618365094e-02 |
+| oct4   | d11  | K9       | 19,406   | 2,811999999999998  | 0,142397922152764589 | 0,090862010483616931 | 4,52910618365094e-02 |
+| oct4   | d15  | K10      | 18,640   | 4,044000000000000  | 0,060622619396358407 | 0,089412757950352861 | 4,08917973218200e-02 |
+| oct4   | d15  | K11      | 18,590   | 2,875999999999999  | 0,136219014026666085 | 0,089412757950352861 | 4,08917973218200e-02 |
+| oct4   | d15  | K12      | 18,441   | 3,808000000000000  | 0,071396640428034092 | 0,089412757950352861 | 4,08917973218200e-02 |
+| oct4   | d16  | K13      | 19,843   | 4,023000000000000  | 0,061511501377112525 | 0,121511212049720957 | 5,39049236892096e-02 |
+| oct4   | d16  | K14      | 19,001   | 2,592000000000002  | 0,165855642574644940 | 0,121511212049720957 | 5,39049236892096e-02 |
+| oct4   | d16  | K15      | 19,310   | 2,866000000000000  | 0,137166492197405399 | 0,121511212049720957 | 5,39049236892096e-02 |
+| sox2   | d0   | L1       | 22,212   | 6,677000000000000  | 0,009772883438384896 | 0,012106883312601676 | 5,00188213381361e-03 |
+| sox2   | d0   | L2       | 22,326   | 6,845000000000001  | 0,008698606392411608 | 0,012106883312601676 | 5,00188213381361e-03 |
+| sox2   | d0   | L3       | 22,554   | 5,808000000000000  | 0,017849160107008523 | 0,012106883312601676 | 5,00188213381361e-03 |
+| sox2   | d7   | L4       | 23,729   | 7,219999999999999  | 0,006707542472169956 | 0,008115146531345131 | 1,23319175000228e-03 |
+| sox2   | d7   | L5       | 23,673   | 6,794999999999998  | 0,009005362084366138 | 0,008115146531345131 | 1,23319175000228e-03 |
+| sox2   | d7   | L6       | 23,762   | 6,856000000000002  | 0,008632535037499301 | 0,008115146531345131 | 1,23319175000228e-03 |
+| sox2   | d11  | L7       | 23,290   | 7,795999999999999  | 0,004499561102927181 | 0,005068258267873239 | 1,39821485937085e-03 |
+| sox2   | d11  | L8       | 23,452   | 7,950000000000001  | 0,004044003608755378 | 0,005068258267873239 | 1,39821485937085e-03 |
+| sox2   | d11  | L9       | 23,824   | 7,230000000000000  | 0,006661210091937160 | 0,005068258267873239 | 1,39821485937085e-03 |
+| sox2   | d15  | L10      | 18,978   | 4,382000000000001  | 0,047960815500027662 | 0,019052009679567623 | 2,50790414471593e-02 |
+| sox2   | d15  | L11      | 23,078   | 7,363999999999999  | 0,006070369287375391 | 0,019052009679567623 | 2,50790414471593e-02 |
+| sox2   | d15  | L12      | 22,955   | 8,321999999999999  | 0,003124844251299816 | 0,019052009679567623 | 2,50790414471593e-02 |
+| sox2   | d16  | L13      | 18,256   | 2,436000000000000  | 0,184795303909230241 | 0,065112130982845073 | 1,03648699316095e-01 |
+| sox2   | d16  | L14      | 23,955   | 7,545999999999999  | 0,005350910077990494 | 0,065112130982845073 | 1,03648699316095e-01 |
+| sox2   | d16  | L15      | 24,034   | 7,590000000000000  | 0,005190178961314499 | 0,065112130982845073 | 1,03648699316095e-01 |
+| Nestin | d0   | M1       | 25,678   | 10,143000000000001 | 0,000884408186540842 | 0,001005919450970835 | 3,78037724925826e-04 |
+| Nestin | d0   | M2       | 25,954   | 10,473000000000001 | 0,000703578978924766 | 0,001005919450970835 | 3,78037724925826e-04 |
+| Nestin | d0   | M3       | 26,196   | 9,450000000000003  | 0,001429771187446897 | 0,001005919450970835 | 3,78037724925826e-04 |
+| Nestin | d7   | M4       | 26,637   | 10,128000000000000 | 0,000893651531374930 | 0,001047338646785763 | 1,49154536320385e-04 |
+| Nestin | d7   | M5       | 26,591   | 9,713000000000001  | 0,001191504404562717 | 0,001047338646785763 | 1,49154536320385e-04 |
+| Nestin | d7   | M6       | 26,792   | 9,886000000000003  | 0,001056860004419641 | 0,001047338646785763 | 1,49154536320385e-04 |
+| Nestin | d11  | M7       | 25,344   | 9,850000000000001  | 0,001083563937566254 | NA                   | NA                   |
+| Nestin | d11  | M8       | 25,548   | 10,045999999999998 | 0,000945916200416630 | NA                   | NA                   |
+| Nestin | d11  | M9       | NA       | NA                 | NA                   | NA                   | NA                   |
+| Nestin | d15  | M10      | 25,146   | 10,550000000000001 | 0,000667011844118357 | 0,040212093347121759 | 6,78034116386107e-02 |
+| Nestin | d15  | M11      | 25,128   | 9,414000000000000  | 0,001465897556166378 | 0,040212093347121759 | 6,78034116386107e-02 |
+| Nestin | d15  | M12      | 17,710   | 3,077000000000002  | 0,118503370641080533 | 0,040212093347121759 | 6,78034116386107e-02 |
+| Nestin | d16  | M13      | 26,670   | 10,850000000000001 | 0,000541781968783127 | 0,000811307199498398 | 2,34037441161003e-04 |
+| Nestin | d16  | M14      | 26,481   | 10,072000000000003 | 0,000929021754230271 | 0,000811307199498398 | 2,34037441161003e-04 |
+| Nestin | d16  | M15      | 26,464   | 10,020000000000000 | 0,000963117875481796 | 0,000811307199498398 | 2,34037441161003e-04 |
+| pax6   | d0   | N1       | 28,141   | 12,605999999999998 | 0,000160404251361007 | 0,000202563640616283 | 9,07049173589390e-05 |
+| pax6   | d0   | N2       | 28,277   | 12,796000000000001 | 0,000140611284466474 | 0,000202563640616283 | 9,07049173589390e-05 |
+| pax6   | d0   | N3       | 28,417   | 11,671000000000003 | 0,000306675386021368 | 0,000202563640616283 | 9,07049173589390e-05 |
+| pax6   | d7   | N4       | 26,551   | 10,041999999999998 | 0,000948542476114878 | 0,001113850118374157 | 2,12530157522733e-04 |
+| pax6   | d7   | N5       | 26,407   | 9,529000000000000  | 0,001353583872705483 | 0,001113850118374157 | 2,12530157522733e-04 |
+| pax6   | d7   | N6       | 26,816   | 9,910000000000000  | 0,001039424006302109 | 0,001113850118374157 | 2,12530157522733e-04 |
+| pax6   | d11  | N7       | 26,240   | 10,745999999999999 | 0,000582279722817692 | 0,000832785029034435 | 3,78505530767820e-04 |
+| pax6   | d11  | N8       | 26,094   | 10,592000000000001 | 0,000647873603807208 | 0,000832785029034435 | 3,78505530767820e-04 |
+| pax6   | d11  | N9       | 26,217   | 9,622999999999998  | 0,001268201760478404 | 0,000832785029034435 | 3,78505530767820e-04 |
+| pax6   | d15  | N10      | 24,989   | 10,393000000000001 | 0,000743695673683233 | 0,000925553902054457 | 4,08653936584204e-04 |
+| pax6   | d15  | N11      | 25,201   | 9,487000000000000  | 0,001393568853240116 | 0,000925553902054457 | 4,08653936584204e-04 |
+| pax6   | d15  | N12      | 25,244   | 10,611000000000001 | 0,000639397179240022 | 0,000925553902054457 | 4,08653936584204e-04 |
+| pax6   | d16  | N13      | 25,234   | 9,414000000000001  | 0,001465897556166376 | 0,118332806864036216 | 2,01592584300493e-01 |
+| pax6   | d16  | N14      | 25,099   | 8,690000000000001  | 0,002421304101443331 | 0,118332806864036216 | 2,01592584300493e-01 |
+| pax6   | d16  | N15      | 17,954   | 1,510000000000002  | 0,351111218934498925 | 0,118332806864036216 | 2,01592584300493e-01 |
+| Foxg1  | d0   | O1       | 27,995   | 12,460000000000001 | 0,000177486879555702 | 0,000282945149618699 | 1,74962623637300e-04 |
+| Foxg1  | d0   | O2       | 27,870   | 12,389000000000001 | 0,000186440124262781 | 0,000282945149618699 | 1,74962623637300e-04 |
+| Foxg1  | d0   | O3       | 27,756   | 11,010000000000002 | 0,000484908445037615 | 0,000282945149618699 | 1,74962623637300e-04 |
+| Foxg1  | d7   | O4       | 27,679   | 11,169999999999998 | 0,000434005215413365 | 0,000523746522152919 | 8,78322810890892e-05 |
+| Foxg1  | d7   | O5       | 27,766   | 10,887999999999998 | 0,000527697950214528 | 0,000523746522152919 | 8,78322810890892e-05 |
+| Foxg1  | d7   | O6       | 27,586   | 10,680000000000000 | 0,000609536400830865 | 0,000523746522152919 | 8,78322810890892e-05 |
+| Foxg1  | d11  | O7       | 27,338   | 11,844000000000001 | 0,000272019934282063 | 0,288184521683127526 | 4,98617302108864e-01 |
+| Foxg1  | d11  | O8       | 27,010   | 11,508000000000001 | 0,000343357714822539 | 0,288184521683127526 | 4,98617302108864e-01 |
+| Foxg1  | d11  | O9       | 16,805   | 0,210999999999999  | 0,863938187400278057 | 0,288184521683127526 | 4,98617302108864e-01 |
+| Foxg1  | d15  | O10      | 26,363   | 11,766999999999999 | 0,000286932697368108 | 0,000345700735619899 | 1,54341824432769e-04 |
+| Foxg1  | d15  | O11      | 26,621   | 10,906999999999998 | 0,000520793838296761 | 0,000345700735619899 | 1,54341824432769e-04 |
+| Foxg1  | d15  | O12      | 26,723   | 12,090000000000000 | 0,000229375671194827 | 0,000345700735619899 | 1,54341824432769e-04 |
+| Foxg1  | d16  | O13      | 26,943   | 11,123000000000001 | 0,000448377032373498 | 0,000619126191915002 | 1,48774900949806e-04 |
+| Foxg1  | d16  | O14      | 26,847   | 10,438000000000002 | 0,000720856643399820 | 0,000619126191915002 | 1,48774900949806e-04 |
+| Foxg1  | d16  | O15      | 26,949   | 10,505000000000003 | 0,000688144899971688 | 0,000619126191915002 | 1,48774900949806e-04 |
+| GAPDH  | d0   | P1       | 15,535   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d0   | P2       | 15,481   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d0   | P3       | 16,746   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d7   | P4       | 16,509   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d7   | P5       | 16,878   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d7   | P6       | 16,906   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d11  | P7       | 15,494   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d11  | P8       | 15,502   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d11  | P9       | 16,594   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d15  | P10      | 14,596   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d15  | P11      | 15,714   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d15  | P12      | 14,633   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d16  | P13      | 15,820   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d16  | P14      | 16,409   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+| GAPDH  | d16  | P15      | 16,444   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
+
 # References
 
-```{=html}
 <!--
@@
 -->
-```
-```{=html}
 <script src="hypothes.is/embed.js" async></script>
-```

### 2024-11-11 manuscript/Manuscript.tex
MS, presentation: edits, update git slide

@@
 
-The references are stored in manuscript/references.bib (need to be
+The references are stored in manuscript/references.bib (needs to be
 defined in the Yaml header). This file will automatically updated when
@@
 can insert them from there. We use knitr::include\_graphics for this.
-The title and legend can also be edited, as will as the width of the
-output figure. Test comment behaviour:
+The title and legend can also be edited, as well as the width of the
+output figure.
 

### 2024-11-11 manuscript/Test_quarto.qmd
MS, presentation: edits, update git slide

--- 2024-06-06 manuscript/table_test.qmd
@@
 ---
-title: "table_test"
+title: "R course report - group 1"
+author: "name1, name2, name3"
 format: html
@@
 ## Quarto
+### Heading 2
+#### Heading 3
 
 Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## Table
-
-|   |   |   |   |   |
-|---|---|---|---|---|
-|   |   |   |   |   |
-|   |   |   |   |   |
-|   |   |   |   |   |
-
-| Reagent type (species) or resource         | Designation                                        | Source or reference                                                                                | Identifiers          | Additional information                                                                                           |
-|--------------------------------------------|----------------------------------------------------|----------------------------------------------------------------------------------------------------|----------------------|------------------------------------------------------------------------------------------------------------------|
-|                                            |                                                    |                                                                                                    |                      |                                                                                                                  |
-| biological sample (N.
-vectensis)           | larval, juvenile and adult N.
-vectensis            | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter           | N/A                  |                                                                                                                  |
-| biological sample (cDNA)                   | cDNA obtained from N.
-vectensis                    | this study                                                                                         | N/A                  | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
-| biological sample (peptide extract)        | peptide extracts obtained from N.
-vectensis        | this study                                                                                         | N/A                  | Peptides extracted from N.
-vectensis according to protocol explained in Material and Methods                     |
-| genetic reagent (cDNA synthesis)           | SuperScript™ III First-Strand Synthesis System     | Invitrogen (from ThermoFisher)                                                                     | 18080051             |                                                                                                                  |
-| genetic reagent (Polymerase)               | Q5® Hot Start High-Fidelity DNA Polymerase         | New England Biolabs                                                                                | M0493L               |                                                                                                                  |
-| genetic reagent (DNA assembly)             | NEBuilder® HiFi DNA Assembly Master Mix            | New England Biolabs                                                                                | E2621L               |                                                                                                                  |
-| genetic reagent (restriction enzyme)       | EcoRV restriction enzyme                           | New England Biolabs                                                                                | R3195L               |                                                                                                                  |
-| genetic reagent (restriction enzyme)       | Afl2 restriction enzyme                            | New England Biolabs                                                                                | R0520L               |                                                                                                                  |
-| genetic reagent (restriction enzyme)       | Hind3 restriction enzyme                           | New England Biolabs                                                                                | R3104L               |                                                                                                                  |
-| genetic reagent (restriction enzyme)       | BamH1 restriction enzyme                           | New England Biolabs                                                                                | R3136L               |                                                                                                                  |
-| genetic reagent (restriction enzyme)       | EcoRI restriction enzyme                           | New England Biolabs                                                                                | R3101L               |                                                                                                                  |
-| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)                                        | Invitrogen (from ThermoFisher)                                                                     | V79020               |                                                                                                                  |
-| recombinant DNA reagent (plasmid)          | pRK5-Gqi9                                          | AddGene                                                                                            | 125711               |                                                                                                                  |
-| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-G5A                                    | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
-| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-Gqi5/9                                 | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
-| recombinant DNA reagent                    | cloned N.
-vectensis GPCRs in pcDNA3.1(+)           | identified in this study                                                                           | N/A                  | full list of cloned GPCRs with sequences in Supplementary file 8                                                 |
-| recombinant DNA reagent                    | synthesized N.
-vectensis GPCRs in pcDNA3.1(+)      | identified in this study, codon optimized and synthesized by GenScript                             | N/A                  | full list of synthesized GPCRs with original and codon optimized sequences in Supplementary file 8               |
-| sequence-based reagent                     | cloning primers to create Gqi5/9                   | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
-| sequence-based reagent                     | GPCR cloning primers                               | this study                                                                                         | N/A                  | full list of primers with sequences in Supplementary file 8                                                      |
-| peptide, recombinant protein               | custom peptides                                    | identified in this study, synthesized by GenScript                                                 | N/A                  | full list of peptides with sequences and purity in Supplementary file 2 and 3                                    |
-| commercial assay or kit (PCR clean up)     | Monarch® PCR & DNA Cleanup Kit (5 μg)              | New England Biolabs                                                                                | T1030L               |                                                                                                                  |
-| commercial assay or kit (Miniprep)         | GeneJET Plasmid Miniprep Kit                       | Thermo Fisher Scientific                                                                           | K0503                |                                                                                                                  |
-| strain, strain background (E.
-coli, TOP10) | One Shot™ TOP10 Chemically Competent E.
-coli       | Thermo Fisher Scientific                                                                           | C404010              | E.
-coli strain used for general cloning                                                                          |
-| cell line (HEK293)                         | HEK293 Cells expressing GFP-AEQUORIN in Cytoplasma | Angio-Proteomie                                                                                    | cAP-0200GFP-AEQ-Cyto |                                                                                                                  |
-| chemical compound, drug                    | DMEM                                               | Gibco (from ThermoFisher)                                                                          | 10566016             |                                                                                                                  |
-| chemical compound, drug                    | OptiMEM                                            | Gibco (from ThermoFisher)                                                                          | 11058021             |                                                                                                                  |
-| chemical compound, drug                    | FBS                                                | Gibco (from ThermoFisher)                                                                          | 10500064             |                                                                                                                  |
-| chemical compound, drug                    | PEI (Polyethylenimine, 25k Mw)                     | Sigma-Aldrich                                                                                      | 408727               | used 0.3 µl of a 1 mg/ml stock solution per 100 ng DNA                                                           |
-| chemical compound, drug                    | Transfectamine 5000                                | AAT Bioquest                                                                                       | 60022                | used 0.3 µl per 100 ng of DNA                                                                                    |
-| chemical compound, drug                    | Coelenterazine-h                                   | Promega                                                                                            | S2011                | diluted to 2 mM in Ethanol and used at a final concentration of 4 µM in the assays                               |
-| chemical compound, drug                    | TRIzol™ Reagent                                    | Invitrogen (from ThermoFisher)                                                                     | 15596026             |                                                                                                                  |
-| other                                      | Corning® 96 Well White Polystyrene Microplate      | Corning (from Sigma-Aldrich)                                                                       | CLS3903              | cell culture treated assay plates                                                                                |
-| other                                      | Nunc™ EasYFlask™ T75 Cell Culture Flasks           | Nunc (from ThermoFisher)                                                                           | 156499               | cell culture flasks                                                                                              |
-| other                                      | Flexstation 3 Multimode Microplate Reader          | Molecular Devices                                                                                  |                      | plate reader                                                                                                     |
-| software, algorithm                        | SoftMax®  Pro 7                                    | Molecular Devices                                                                                  |                      |                                                                                                                  |
-| software, algorithm                        | R                                                  | https://cran.rstudio.com/                                                                          |                      |                                                                                                                  |
-| software, algorithm                        | RStudio                                            | https://posit.co/download/rstudio-desktop/                                                         |                      |                                                                                                                  |
-| software, algorithm                        | SignalP4.1                                         | https://services.healthtech.dtu.dk/services/SignalP-6.0/                                           |                      |                                                                                                                  |
-| software, algorithm                        | NeuroPID                                           | https://bio.tools/neuropid                                                                         |                      |                                                                                                                  |
-| software, algorithm                        | HMMER3.1b2                                         | http://hmmer.org/download.html                                                                     |                      |                                                                                                                  |
-| software, algorithm                        | CD-HIT                                             | https://sites.google.com/view/cd-hit                                                               |                      |                                                                                                                  |
-| software, algorithm                        | TransDecoder                                       | https://github.com/TransDecoder/TransDecoder                                                       |                      |                                                                                                                  |
-| software, algorithm                        | CLANS (desktop version)                            | https://mybiosoftware.com/clans-20101007-visualize-protein-families-based-pairwise-similarity.html |                      |                                                                                                                  |
-| software, algorithm                        | CLANS (online toolkit)                             | https://toolkit.tuebingen.mpg.de/tools/clans                                                       |                      |                                                                                                                  |
-| software, algorithm                        | Phobius                                            | https://phobius.sbc.su.se/data.html                                                                |                      |                                                                                                                  |
-| software, algorithm                        | muscle alignment tool                              | https://drive5.com/muscle5/                                                                        |                      |                                                                                                                  |
-| software, algorithm                        | MAFFT v7                                           | https://mafft.cbrc.jp/alignment/software/                                                          |                      |                                                                                                                  |
-| software, algorithm                        | trimAl                                             | http://trimal.cgenomics.org/trimal                                                                 |                      |                                                                                                                  |
-| software, algorithm                        | IQ-tree2                                           | http://www.iqtree.org/                                                                             |                      |                                                                                                                  |
-| software, algorithm                        | Fasttree                                           | http://www.microbesonline.org/fasttree/                                                            |                      |                                                                                                                  |
 
@@
 When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
+
+```{r}
+print('hi, this is an R command executed')
+```
+
+```{bash}
+echo hi
+```
 
@@
 #| echo: false
+#| eval: true
 2 * 2
@@
 The `echo: false` option disables the printing of code (only output is displayed).
+
+## Next section

### 2024-11-11 presentation/RStudio_paper_writing_course_presentation.qmd
MS, presentation: edits, update git slide

@@
 
-## Part 6 - Collaborative code and paper writing with Rstudio and GitHub
-
-<br>
-
--   GitHub www.github.com is a platform for software development and version control
--   owned by Microsoft since 2018
+## Part 6 - Collaborative code and paper writing with Rstudio and git
+
+<br>
+
+-   git is an open source program and protocol for version control
+- several online platforms were built to make code sharing with git easier
+- GitHub www.github.com is one such platform
+- GitHub is owned by Microsoft since 2018
 - developers can have public and private repositories
@@
 - integrates well with Rstudio
--   uses git protocol that is open source and also used by other code-hosting sites
 

### 2024-11-11 analysis/scripts/Course_exercises.R

@@ -40,10 +40,10 @@ writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
 # load data ---------------------------------------------------------------
 
 data_Jose <- readxl::read_excel("analysis/data/data - José - March 2024.xlsx")
-
+data_Jose
 # alternatively, use the rio package with import() to automatically recognise format and import
 data_Jose <- rio::import("analysis/data/data - José - March 2024.xlsx")
-
+data_Jose
 
 # rio: A Swiss-Army Knife for Data I/O  -----------------------------------
 
@@ -141,19 +141,23 @@ data_Syn_clean <- data_Syn  %>%
   rename_with(~ gsub("...", "_", .x, fixed = TRUE))
 
 tb_syn <- data_Syn_clean |>
-  pivot_longer(matches("aSyn"), 
-               names_to = c("condition", "sample"), 
-               names_sep = "_",
-               values_to = "fluorescence")
+  pivot_longer(
+    matches("aSyn"), 
+    names_to = c("condition", "sample"), 
+    names_sep = "_",
+    values_to = "fluorescence"
+    )
 
 plot_syn <- tb_syn %>%
   ggplot(aes(x = Time, y = fluorescence, color = condition)) +
   geom_smooth(
     method = 'loess', span = 0.1
     ) +
-  theme_minimal()
-plot_syn
+  theme_minimal()  +
+  facet_wrap(~condition)
 
+plot_syn
+theme()
 plot_syn +
   annotate("segment", x = 20, xend = 50, y = 1, yend = 1, linewidth = 1)+
   annotate("text", x = 34, y = 300, label = "30 sec", size = 3)
@@ -163,9 +167,10 @@ plot_syn +
 head(iris)
 iris
 iris %>%
-  ggplot(aes(x = Petal.Length, y = Sepal.Width, color = Species)) +
+  ggplot(aes(x = Petal.Length, y = Sepal.Width, fill = Species)) +
   geom_boxplot(notch = TRUE) +
-  theme_minimal()
+  theme_minimal() +
+  guides(fill = guide_legend(title = "genus")) 
 
 iris %>%
   ggplot(aes(x = Petal.Length)) +
@@ -176,7 +181,7 @@ iris %>%
     x = Petal.Length, y = Sepal.Width, 
[…]

### 2024-11-11 analysis/scripts/packages_and_functions.R

@@ -35,4 +35,13 @@ writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
 
 # functions of general use ---------------
 
+# arrows and other line tags -----------
 
+#define arrow endpoints 
+
+arrow_coords <- data.frame(x1 = 0.95, x2 = 0.95, y1 = 0.8, y2 = 0.9)
+arrow <- geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrow_coords, 
+                      arrow = arrow(ends = "both", type = "closed", length = unit(0.1,"cm")),
+                      lineend = "butt",
+                      linejoin = "mitre",
+                      arrow.fill = "black", linewidth = 0.2)
